### 2013-03-04 proposal.tex
added our proposal

% Juneki Hong and Michael Tango
% Declarative Methods
% Professor Eisner
% March 4, 2013

\documentclass{article}
\author{Juneki Hong and Michael Tango}
\title{Declarative Methods Project Proposal: \\ JumanG}
\usepackage[ampersand]{easylist}

\begin{document}

\maketitle

\newpage

\section{Introduction}
We will be creating a declarative language for Data Visualization. Given a set of data, and optionally some high level descriptions/constraints for how to display this data, we want to generate a representation of this data in a nice “pretty” way. At this time, we want to primarily focus on handling graphs. As loftier goals, it would also be nice to support charts and plots as well.

A typical usecase might be as follows: 
The user wants to visualize a graph such that the edges of the nodes cross as least as possible and all of the nodes are 3-colored. The user specifies these things and then provides an adjacency list. JumanG would come up with a nice ordering of the nodes that could be output and displayed.

\section{Frontend}
People will be able to make their own JumanG files, or .jm files that will encode a command to be carried out by JumanG.

These files should have in this order:

\begin{easylist}[enumerate]
& A specification of what type of visualization is needed.

We will work on graphs first, but we do want to have options for charts and plots if can get to them later

& Constraints for the visualization (Optional). Examples might include:

	&& coloring all cliques of size 4 with orange

	&& labeling the nodes in topological order if possible

& Specifications for the output (Optional). Examples might include:

	&& output the resulting graph into tikz format (for easy use in LaTeX)

	&& generate a 500x500 .jpg file

& The data itself (or a file path to the data).

\end{easylist}

Anything not specified in the Constraints or Specifications section will observe default behavior. If applicable, when given no constraints or specifications are given, we also want JumanG to intelligently chose its own.

\section{Backend}

For the backend, we would like build on top of Graphviz in terms of displaying and manipulating graphs. Graphviz is a package that has lots of options when it comes to visualizing graphs, and we will try to take advantage of these and provide an interface with the user. For charts and plots, we want to use Scipy. Similar to Graphviz, it is an extensive library that we could use.

For a programming language, our current plan is to build our project in Python. Professor Eisner has suggested that our project might integrate into Dyna as well.

\end{document}

### 2013-03-04 clean.sh
added a clean.sh script

@@ -1,0 +1,1 @@
+rm *.aux *.log

### 2013-04-26 proposal/proposal2.tex
moved files around a little

% Juneki Hong and Michael Tango
% Declarative Methods
% Professor Eisner
% March 4, 2013

\documentclass{article}
\author{Juneki Hong and Michael Tango}
\title{Declarative Methods Project Proposal: \\ JumanG}
\usepackage[ampersand]{easylist}

\begin{document}

\maketitle

VERSION 2

\newpage

\subsection*{Introduction}

We will be creating a declarative language for Data Visualization. Specifically for visualizing dynamically changing graphs.
JumanG will be able to derive a graph out of specifications over data, and redraw the graph whenever the specifications change.

\subsection*{Frontend}

According to Tim, a “change” in a graph should in reality be a change to the underlying data that the graph represents. Because of this, we would want JumanG be a language about relationships between data. Each variable declaration would specify a piece of data and its attributes. For example:

\begin{verbatim}
// Alice, Bob, and Casper are data that have these attributes
Alice   [type: human, foo: bar, foods:  [apples, broccoli, cherries]] 
Bob     [type: human, foo: baz, colors: [agenta, blue, curquoise]]
Casper  [type: supernatural]

// We could draw edges based on attributes or do it on a node-by-node basis.
Bob -> [type: human]
[foods: apples] -> [foo: baz]
Bob -> Casper
\end{verbatim}
We would also be able to print out any node and see its attributes. Or print out an edge and see the attributes that activated it.

There are a lot of issues that we could choose to solve with this project. we could color or position the generated nodes in a way that might better represent the attributes in the data. For example, if a lot of nodes with certain attributes happen to be connected together, we would want to try and recognize that by coloring them all similarly.

\subsection*{Use Cases}
Here are some possible interesting usecases:

-Representing and maintaining someone's social network of friends as a graph, and changing this graph simply by altering the attributes of particular people. This data could be pulled automatically from someone’s profile to update the graph in real time.

Taking a list of people and grouping them based on personality trait attributes. Each personality trait would be a node, and the strength of the edges between nodes would reflect how many people had both traits.

\subsection*{Backend}

For the backend, we would like build on top of Graphviz in terms of displaying and manipulating graphs. 
For a programming language, our current plan is to build our project in Python.

\end{document}

### 2013-04-28 Graph.py
Added Radial display; added position information Nodes

@@ -6,6 +6,8 @@ class Node:
     def __init__(self, name, label=None):
         self.Name = name
         self.Label = label
+        self.PosX = 0
+        self.PosY = 0
         self.Attributes = {}
 
     def __str__(self):

### 2013-04-28 RadialDisplay.py

@@ -1,0 +1,37 @@
+from Graph import *
+from Utils import *
+from math import cos, sin, radians
+
+# @Graph: graph to be sorted
+# @Sink: If the sink should be the center, rather than the source
+def __recRadial(graph, root, degrees, start, layer):
+
+	children = graph.AdjacencyList[root]
+
+	subDeg = degrees / len(children)
+	currentDegrees = start
+
+	for c in children:
+		c.PosX = layer*5 * cos(radians(currentDegrees+(subDeg/2)))
+		c.PosY = layer*5 * sin(radians(currentDegrees+(subDeg/2)))
+		__recRadial(graph, c, subDeg, currentDegrees, layer+1)
+		currentDegrees += subDeg
+
+
+
+def radialAssign(graph, sink = False):
+
+	gSorted = list()
+
+	# Toposort goes HERE:
+	# gSorted = topolayer(graph)
+
+
+	gSorted[0].PosX=0
+	gSorted[0].PosY=0
+
+	# TODO: Add support for multiple roots
+
+	__recRadial(graph, gSorted[0], 360, 0, 1)
+
+

### 2013-04-28 GraphAnalysis.py
My Graph Analysis file so far

@@ -1,0 +1,66 @@
+#!/usr/bin/python
+
+from collections import deque
+from DotParser import *
+
+
+class GraphAnalysis:
+    def __init__(self, graph):
+        self.Graph = graph
+        self.RootNode = None
+        self.DependencyTable = self.buildDependencyTable(self.Graph)
+
+
+    def buildDependencyTable(self, graph):
+        return None
+
+
+    def BFS(self, root):
+        DISPLAYSTEPS = False
+
+        queue = deque()
+        queue.append(root)
+        
+        if DISPLAYSTEPS:
+            print "ROOT",root
+            print
+        
+        visited = {}
+        visited[root] = True
+        
+        while queue:
+            node = queue.popleft()
+            children = self.Graph.AdjacencyList[node]
+            
+            if DISPLAYSTEPS:
+                print "CURRENT NODE: ",node
+
+            for child in children:
+                childNode = child[0]
+                
+                if DISPLAYSTEPS:
+                    print "CHILD: ", childNode
+                if not visited.get(childNode,False):
+                    visited[childNode] = True
+                    queue.append(childNode)
+                    if DISPLAYSTEPS:
+                        print "PUSHED: ", childNode
+            if DISPLAYSTEPS:
+                print
+
+
+
+if __name__ == "__main__":
+    parser = DotParser()
+
+    filename = argv[1]
+    parser.readFile(filename)
+    graph = parser.Graph
+
+    analysis = GraphAnalysis(graph)
+
+    print graph
+
+    arbitraryRoot = graph.NodeList.keys()[0]
+    analysis.BFS(arbitraryRoot)
+    

### 2013-04-29 TikzWriter.py
Added Tikz Drawer

@@ -1,0 +1,29 @@
+from Graph import *
+
+def tikGraph(graph, l = None):
+	output = ""
+	oputput += "% Tik output from JumanG\n"
+	output += "\\documentclass{article}\n"
+	output += "\\usepackage{tikz}\n"
+	output += "\\pagestyle{empty}\n"
+	output += "\\usepackage{verbatim}\n"
+	output += "\\begin{document}\n"
+	output += "\\begin{tikzpicture}[scale=.9, transform shape]\n"
+	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
+
+	for n in graph.NodeList:
+		output+="\t\\node ("+n.Name+") at ("+n.Posx+", "+n.PosY+") {"+n.Name+"};\n"
+
+	for n1 in graph.NodeList:
+		for n2 in graph.AdjacencyList[n1]:
+			output+="\t\\draw [->] ("+n1.Name+")--("+n2.Name+");\n"
+
+	output += "\\end{tikzpicture}\n"
+	output += "\\end{document}\n"
+
+	if l:
+		f=open(l, "r")
+		f.write(output)
+
+	else:
+		print output

### 2013-04-29 dot/dotDisplay.sh
dotDisplay.sh

@@ -1,0 +1,3 @@
+#!/bin/sh
+
+dot -Tpng $1.dot -o $1.png ; eog $1.png

### 2013-04-29 GraphAnalysis.py
Graph Analysis. Has implementation that gets the root nodes.

@@ -1,5 +1,6 @@
 #!/usr/bin/python
 
+from sys import *
 from collections import deque
 from DotParser import *
 
@@ -12,7 +13,37 @@ class GraphAnalysis:
 
 
     def buildDependencyTable(self, graph):
-        return None
+        dependencyTable = {}
+        
+        for node in self.Graph.AdjacencyList:
+            edgeList = self.Graph.AdjacencyList[node]
+            for (node2,Type) in edgeList:
+                dependencyTable[node2] = dependencyTable.get(node2,[])
+                dependencyTable[node2].append(node)
+        
+
+        '''
+        print "dependency Table: "
+        string = ""
+        for node in dependencyTable:
+            string = string + node.__str__() + ": "
+
+            dependencyList = dependencyTable[node]
+            for dependency in dependencyList:
+                string = string + dependency.__str__() + " "
+                
+            string = string + "\n"
+        print string
+        '''
+        return dependencyTable
+
+
+    def getRootNodes(self):
+        rootList = []
+        for node in self.Graph.NodeList:
+            if node not in self.DependencyTable:
+                rootList.append(node)
+        return rootList
 
 
     def BFS(self, root):
@@ -30,7 +61,10 @@ class GraphAnalysis:
         
         while queue:
             node = queue.popleft()
-            children = self.Graph.AdjacencyList[node]
+            children = self.Graph.AdjacencyList.get(node,None)
+            
+            if children == None:
+                continue
             
             if DISPLAYSTEPS:
                 print "CURRENT NODE: ",node
@@ -64,3 +98,8 @@ if __name__ == "__main__":
     arbitraryRoot = graph.NodeList.keys()[0]
     analysis.BFS(arbitraryRoot)
     
+    
+    print "ROOTS"
+    rootList = analysis.getRootNodes()
+    for root in rootList:
+        print root

### 2013-04-29 GraphAnalysis.py
topological sort implemented

@@ -19,24 +19,21 @@ class GraphAnalysis:
             edgeList = self.Graph.AdjacencyList[node]
             for (node2,Type) in edgeList:
                 dependencyTable[node2] = dependencyTable.get(node2,[])
-                dependencyTable[node2].append(node)
-        
+                dependencyTable[node2].append(node)        
+        return dependencyTable
 
-        '''
+    def printDependencyTable(self):
         print "dependency Table: "
         string = ""
-        for node in dependencyTable:
+        for node in self.DependencyTable:
             string = string + node.__str__() + ": "
-
-            dependencyList = dependencyTable[node]
+            
+            dependencyList = self.DependencyTable[node]
             for dependency in dependencyList:
                 string = string + dependency.__str__() + " "
                 
             string = string + "\n"
         print string
-        '''
-        return dependencyTable
-
 
     def getRootNodes(self):
         rootList = []
@@ -44,6 +41,27 @@ class GraphAnalysis:
             if node not in self.DependencyTable:
                 rootList.append(node)
         return rootList
+
+
+    def topologicalSort(self):
+        dependencyTable = self.buildDependencyTable(self.Graph)
+
+        queue = self.getRootNodes()
+        topoSort = []
+
+        while queue:
+            n = queue.pop()
+            topoSort.append(n)
+
+            adjacencies = self.Graph.AdjacencyList.get(n,None)
+            if not adjacencies == None: 
+                for (adjacency,edgeType) in adjacencies:
+                    #print adjacency
+                    dependencyTable.get(adjacency).remove(n)
+                    if not dependencyTable.get(adjacency):
+                        queue.append(adjacency)
+
+        return topoSort
 
 
     def BFS(self, root):
@@ -98,8 +116,17 @@ if __name__ == "__main__":
     arbitraryRoot = graph.NodeList.keys()[0]
     analysis.BFS(arbitraryRoot)
     
+    analysis.printDependencyTable
     
-    print "ROOTS"
+    print "ROOTS:"
     rootList = analysis.getRootNodes()
     for root in rootList:
         print root
+    print
+    
+
+    topoList = analysis.topologicalSort()
+    print "TOPOLOGICAL SORT:"
+    for node in topoList:
+        print node
+    print

### 2013-04-29 BasicDriver.py
driver and fixes

@@ -1,0 +1,28 @@
+from Graph import *
+import RadialDisplay as RD
+import TikzWriter as TW
+import sys
+from DotParser import *
+
+argv = sys.argv
+
+infile = ""
+outfile = ""
+if len(argv) !=3 :
+	print "Usage: BasicDriver inputfile outputfile"
+	sys.exit()
+
+else:
+	infile = argv[1]
+	outfile = argv[2]
+
+DP = DotParser()
+
+DP.readFile(infile)
+graph = DP.Graph
+
+RD.radialAssign(graph)
+
+TW.tikGraph(graph, outfile)
+
+

### 2013-04-29 Graph.py

@@ -11,7 +11,7 @@ class Node:
         self.Attributes = {}
 
     def __str__(self):
-        result = "[" + self.Name + "]"
+        result = "[" + self.Name + "] @(" + str(self.PosX)+","+str(self.PosY)+")"
 
         if self.Attributes:
             result = result + "\t"
@@ -31,6 +31,9 @@ class Node:
     def __hash__(self):
         return hash(self.Name)
 
+    def __repr__(self):
+        return self.__str__()
+
 class Edge:
    def __init__(self, n1, n2, dirType):
       self.Node1 = n1
@@ -46,6 +49,9 @@ class Edge:
               result = result + attribute + ": " + self.Attributes[attribute] + ", "
 
       return result
+
+   def __repr__(self):
+      return self.__str__()
 
 typeDict = {
    0:0,
@@ -66,6 +72,8 @@ class EdgeType:
 
    def __str__(self):
       return displayDict[self.Type]
+   def __repr__(self):
+      return self.__str__()
 
 
 
@@ -113,3 +121,6 @@ class Graph:
         result = result + "}\n"
        
         return result
+
+    def __repr__(self):
+        return self.__str__()

### 2013-04-29 RadialDisplay.py

@@ -1,19 +1,36 @@
 from Graph import *
 from Utils import *
+from GraphAnalysis import *
 from math import cos, sin, radians
+
+
+armLength = 5
 
 # @Graph: graph to be sorted
 # @Sink: If the sink should be the center, rather than the source
 def __recRadial(graph, root, degrees, start, layer):
 
-	children = graph.AdjacencyList[root]
+	if root in graph.AdjacencyList.keys():
+		children = graph.AdjacencyList[root]
+
+	else:
+		return
 
 	subDeg = degrees / len(children)
 	currentDegrees = start
 
-	for c in children:
-		c.PosX = layer*5 * cos(radians(currentDegrees+(subDeg/2)))
-		c.PosY = layer*5 * sin(radians(currentDegrees+(subDeg/2)))
+	for (c, t) in children:
+		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
+		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
+
+		if x < .00001:
+			x = 0.0
+		if y < .00001:
+			y = 0.0
+
+		c.PosX = x
+		c.PosY = y
+
 		__recRadial(graph, c, subDeg, currentDegrees, layer+1)
 		currentDegrees += subDeg
 
@@ -24,14 +41,18 @@ def radialAssign(graph, sink = False):
 	gSorted = list()
 
 	# Toposort goes HERE:
-	# gSorted = topolayer(graph)
+	GA = GraphAnalysis(graph)
 
+	gSorted = GA.topologicalSort()
 
 	gSorted[0].PosX=0
 	gSorted[0].PosY=0
+	# root.PosX=0
+	# root.PosY=0
 
 	# TODO: Add support for multiple roots
 
 	__recRadial(graph, gSorted[0], 360, 0, 1)
+	# __recRadial(graph, root, 360,0,1)
 
 

### 2013-04-29 TikzWriter.py

@@ -2,7 +2,7 @@ from Graph import *
 
 def tikGraph(graph, l = None):
 	output = ""
-	oputput += "% Tik output from JumanG\n"
+	output += "% Tik output from JumanG\n"
 	output += "\\documentclass{article}\n"
 	output += "\\usepackage{tikz}\n"
 	output += "\\pagestyle{empty}\n"
@@ -12,17 +12,22 @@ def tikGraph(graph, l = None):
 	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
 
 	for n in graph.NodeList:
-		output+="\t\\node ("+n.Name+") at ("+n.Posx+", "+n.PosY+") {"+n.Name+"};\n"
+		output+="\t\\node ("+n.Name+") at ("+str(n.PosX)+", "+str(n.PosY)+") {"+n.Name+"};\n"
 
 	for n1 in graph.NodeList:
-		for n2 in graph.AdjacencyList[n1]:
-			output+="\t\\draw [->] ("+n1.Name+")--("+n2.Name+");\n"
+		if n1 in graph.AdjacencyList.keys():
+			for (n2, t) in graph.AdjacencyList[n1]:
+				if t.Type==1:
+					output+="\t\\draw [->] ("+n1.Name+")--("+n2.Name+");\n"
+				else:
+					output+="\t\\draw [-] ("+n1.Name+")--("+n2.Name+");\n"
+
 
 	output += "\\end{tikzpicture}\n"
 	output += "\\end{document}\n"
 
 	if l:
-		f=open(l, "r")
+		f=open(l, "w")
 		f.write(output)
 
 	else:

### 2013-04-29 DotParser.py
changed how nodes are stored in my graph data structures

@@ -7,8 +7,6 @@ from Graph import *
 class DotParser:
 
    def __init__(self):
-      #self.EdgeList = []
-      #self.NodeList = []
       self.Graph = Graph()
 
    def readFile(self, filename):
@@ -90,6 +88,7 @@ class DotParser:
             self.Graph.addEdge(e1)
             self.Graph.addEdge(e2)
          elif "[" in line and "]" in line:
+            #Information about the node
             (line,attributes) = stripAttributes(line)            
             name = line.strip()
             n = Node(name)
@@ -99,6 +98,8 @@ class DotParser:
 
       for n in self.Graph.AdjacencyList:
          self.Graph.addNode(n)
+      return self.Graph
+
 
 if __name__ ==  "__main__":
    parser = DotParser()
@@ -121,9 +122,9 @@ if __name__ ==  "__main__":
 
    #try:
    filename = argv[1]
-   parser.readFile(filename)
+   graph = parser.readFile(filename)
 
-   print parser.Graph
+   print graph
 
 #   except(IndexError):
 #      print "ERROR: No file given"

### 2013-04-29 Graph.py

@@ -80,20 +80,45 @@ class EdgeType:
 
 class Graph:
     def __init__(self, name = None):
-        self.NodeList = {}
+        #self.NodeList = {}
         self.AdjacencyList = {}
         self.Name = name
         
+    def getNodeList(self):
+        return self.AdjacencyList.keys()
 
     def addNode(self, n):
-        if self.NodeList.get(n,None) == None:
-            self.NodeList[n] = True
+        #if self.NodeList.get(n,None) == None:
+        #    self.NodeList[n] = True
+        if self.AdjacencyList.get(n,None) == None:
+            self.AdjacencyList[n] = []
+        else:
+            index = self.AdjacencyList.keys().index(n)
+            node = self.AdjacencyList.keys()[index]
+            node.Name = n.Name
+            node.Attributes = n.Attributes
+            node.Label = n.Label
+            node.PosX = n.PosX
+            node.PosY = n.PosY
 
     def addEdge(self, e):
-        if self.AdjacencyList.get(e.Node1,None) == None:
+        #If both node1 and node2 of the edge does not exist:
+        if self.AdjacencyList.get(e.Node1,None) == None and self.AdjacencyList.get(e.Node2,None) == None:
+            self.AdjacencyList[e.Node2] = []
             self.AdjacencyList[e.Node1] = [(e.Node2, e.Type)]
-        else:
+        # If node1 does not exist and node2 does:
+        elif self.AdjacencyList.get(e.Node1,None) == None:
+            node2 = self.AdjacencyList.keys().get(e.Node2)
+            self.AdjacencyList[e.Node1] = [(node2, e.Type)]
+        # If node2 does not exist and node1 does: 
+        elif self.AdjacencyList.get(e.Node2,None) == None:
+            self.AdjacencyList[e.Node2] = []
             self.AdjacencyList[e.Node1].append((e.Node2, e.Type))
+        # Else, both exist:
+        else:
+            index = self.AdjacencyList.keys().index(e.Node2)
+            node2 = self.AdjacencyList.keys()[index]
+            self.AdjacencyList[e.Node1].append((node2, e.Type))
 
 
     def __str__(self):
@@ -105,7 +130,7 @@ class Graph:
         result = result + "\n"
         result = result + "Nodes: \n"
         
-        for n1 in self.NodeList:
+        for n1 in self.AdjacencyList.keys():
             result = result + n1.__str__()
 
         result = result + "\n\n"

### 2013-04-29 GraphAnalysis.py
fixed GraphAnalysis.py based on my change to nodelist

@@ -37,7 +37,7 @@ class GraphAnalysis:
 
     def getRootNodes(self):
         rootList = []
-        for node in self.Graph.NodeList:
+        for node in self.Graph.getNodeList():
             if node not in self.DependencyTable:
                 rootList.append(node)
         return rootList
@@ -113,7 +113,7 @@ if __name__ == "__main__":
 
     print graph
 
-    arbitraryRoot = graph.NodeList.keys()[0]
+    arbitraryRoot = graph.getNodeList()[0]
     analysis.BFS(arbitraryRoot)
     
     analysis.printDependencyTable

### 2013-04-29 RadialDisplay.py
YEAHHHHHHHHHHHHHH

@@ -10,10 +10,9 @@ armLength = 5
 # @Sink: If the sink should be the center, rather than the source
 def __recRadial(graph, root, degrees, start, layer):
 
-	if root in graph.AdjacencyList.keys():
-		children = graph.AdjacencyList[root]
+	children = graph.AdjacencyList[root]
 
-	else:
+	if len(children) ==0:
 		return
 
 	subDeg = degrees / len(children)
@@ -23,9 +22,9 @@ def __recRadial(graph, root, degrees, start, layer):
 		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
 		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
 
-		if x < .00001:
+		if abs(x)< .00001:
 			x = 0.0
-		if y < .00001:
+		if abs(y) < .00001:
 			y = 0.0
 
 		c.PosX = x

### 2013-04-29 TikzWriter.py

@@ -11,16 +11,15 @@ def tikGraph(graph, l = None):
 	output += "\\begin{tikzpicture}[scale=.9, transform shape]\n"
 	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
 
-	for n in graph.NodeList:
+	for n in graph.getNodeList():
 		output+="\t\\node ("+n.Name+") at ("+str(n.PosX)+", "+str(n.PosY)+") {"+n.Name+"};\n"
 
-	for n1 in graph.NodeList:
-		if n1 in graph.AdjacencyList.keys():
-			for (n2, t) in graph.AdjacencyList[n1]:
-				if t.Type==1:
-					output+="\t\\draw [->] ("+n1.Name+")--("+n2.Name+");\n"
-				else:
-					output+="\t\\draw [-] ("+n1.Name+")--("+n2.Name+");\n"
+	for n1 in graph.getNodeList():
+		for (n2, t) in graph.AdjacencyList[n1]:
+			if t.Type==1:
+				output+="\t\\draw [->] ("+n1.Name+")--("+n2.Name+");\n"
+			else:
+				output+="\t\\draw [-] ("+n1.Name+")--("+n2.Name+");\n"
 
 
 	output += "\\end{tikzpicture}\n"

### 2013-04-29 RadialDisplay.py
stuffz

@@ -5,6 +5,7 @@ from math import cos, sin, radians
 
 
 armLength = 5
+visited = list()
 
 # @Graph: graph to be sorted
 # @Sink: If the sink should be the center, rather than the source
@@ -19,6 +20,9 @@ def __recRadial(graph, root, degrees, start, layer):
 	currentDegrees = start
 
 	for (c, t) in children:
+		if c in visited:
+			continue
+		visited.append(c)
 		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
 		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
 
@@ -38,12 +42,14 @@ def __recRadial(graph, root, degrees, start, layer):
 def radialAssign(graph, sink = False):
 
 	gSorted = list()
+	visited = list()
 
 	# Toposort goes HERE:
 	GA = GraphAnalysis(graph)
 
 	gSorted = GA.topologicalSort()
-
+	if len(gSorted)<1:
+		gSorted.append(graph.getNodeList()[0])
 	gSorted[0].PosX=0
 	gSorted[0].PosY=0
 	# root.PosX=0

### 2013-04-29 TikzWriter.py

@@ -12,7 +12,7 @@ def tikGraph(graph, l = None):
 	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
 
 	for n in graph.getNodeList():
-		output+="\t\\node ("+n.Name+") at ("+str(n.PosX)+", "+str(n.PosY)+") {"+n.Name+"};\n"
+		output+="\t\\node ("+n.Name+") at ("+"{0:.2f}".format(n.PosX)+", "+"{0:.2f}".format(n.PosY)+") {"+n.Name+"};\n"
 
 	for n1 in graph.getNodeList():
 		for (n2, t) in graph.AdjacencyList[n1]:

### 2013-04-30 Utils.py
utils

@@ -2,6 +2,7 @@
 
 from pprint import pprint
 from sys import argv
+from copy import deepcopy
 
 
 def stripAttributes(line):

### 2013-04-30 Graph.py
added copy functions

@@ -1,6 +1,7 @@
 #!/usr/bin/python
 
-from pprint import pprint
+from Utils import *
+
 
 class Node:
     def __init__(self, name, label=None):
@@ -9,21 +10,31 @@ class Node:
         self.PosX = 0
         self.PosY = 0
         self.Attributes = {}
+        
+    def copy(self):
+        name = self.Name
+        label = self.Label
 
+        node = Node(name, label)
+        node.PosX = self.PosX
+        node.PosY = self.PosY
+        node.Attributes = copy.deepcopy(self.Attributes)
+        return node
+        
+        
+        
     def __str__(self):
         result = "[" + self.Name + "] @(" + str(self.PosX)+","+str(self.PosY)+")"
-
+        
         if self.Attributes:
             result = result + "\t"
             for attribute in self.Attributes:
                 result = result + attribute + ": " + self.Attributes[attribute]+ ", "
-            result = result + "\n"
-
+            result = result
         return result 
 
     def __eq__(self, other):
         return self.Name == other.Name
-
 
     def __neq__(self, other):
         return not self.__eq__(other)
@@ -35,23 +46,31 @@ class Node:
         return self.__str__()
 
 class Edge:
-   def __init__(self, n1, n2, dirType):
-      self.Node1 = n1
-      self.Node2 = n2
-      self.Type = EdgeType(dirType)
-      self.Attributes = {}
+    def __init__(self, n1, n2, dirType):
+        self.Node1 = n1
+        self.Node2 = n2
+        self.Type = EdgeType(dirType)
+        self.Attributes = {}
 
-   def __str__(self):
-      result =  "[" + self.Node1.Name + self.Type.__str__() + self.Node2.Name + "]"
-      if self.Attributes:
-          result = result + "\t"
-          for attribute in self.Attributes:
-              result = result + attribute + ": " + self.Attributes[attribute] + ", "
+    def copy(self):
+        node1 = self.Node1.copy()
+        node2 = self.Node2.copy()
+        dirType = self.Type.copy()
 
-      return result
+        edge = Edge(node1, node2, dirType)
+        edge.Attributes = copy.deepcopy(self.Attributes)
+        return edge
 
-   def __repr__(self):
-      return self.__str__()
+    def __str__(self):
+        result =  "[" + self.Node1.Name + self.Type.__str__() + self.Node2.Name + "]"
+        if self.Attributes:
+            result = result + "\t"
+            for attribute in self.Attributes:
[…]

### 2013-04-30 Graph.py
Graph distance and stuff

@@ -1,6 +1,7 @@
 #!/usr/bin/python
 
 from pprint import pprint
+from math import sqrt
 
 class Node:
     def __init__(self, name, label=None):
@@ -149,3 +150,10 @@ class Graph:
 
     def __repr__(self):
         return self.__str__()
+
+    @staticmethod
+    def nodeDist(n1, n2):
+        x = n1.PosX - n2.PosX
+        y = n1.PosY - n2.PosY
+        return sqrt(x**2 + y**2)
+

### 2013-04-30 NBodyRepositioner.py

@@ -1,0 +1,24 @@
+from Graph import *
+from Utils import *
+from sys import floatinfo
+
+bestCopy = None
+minForce = floatinfo.max
+
+def __calcForce(graph):
+	for 
+
+def __jitter(graph):
+	tHold = graph.copy()
+
+
+def reposition(graph):
+	bestCopy = graph.copy()
+
+	for x in xrange(1000):
+		(graph, m) = __jitter(graph).copy()
+		if m < minForce:
+			bestCopy = graph.copy()
+			minForce = m
+
+	return bestCopy

### 2013-04-30 RadialDisplay.py

@@ -4,7 +4,7 @@ from GraphAnalysis import *
 from math import cos, sin, radians
 
 
-armLength = 5
+armLength = 3
 visited = list()
 
 # @Graph: graph to be sorted

### 2013-04-30 GraphAnalysis.py
Added a couple more things to graph analysis. Will now count the number of nodes and edges

@@ -44,8 +44,7 @@ class GraphAnalysis:
 
 
     def topologicalSort(self):
-        dependencyTable = self.buildDependencyTable(self.Graph)
-
+        #dependencyTable = self.buildDependencyTable(self.Graph)
         queue = self.getRootNodes()
         topoSort = []
 
@@ -57,10 +56,10 @@ class GraphAnalysis:
             if not adjacencies == None: 
                 for (adjacency,edgeType) in adjacencies:
                     #print adjacency
-                    dependencyTable.get(adjacency).remove(n)
-                    if not dependencyTable.get(adjacency):
+                    self.DependencyTable.get(adjacency).remove(n)
+                    if not self.DependencyTable.get(adjacency):
                         queue.append(adjacency)
-
+        self.DependencyTable = self.buildDependencyTable(self.Graph)
         return topoSort
 
 
@@ -71,18 +70,14 @@ class GraphAnalysis:
         queue.append(root)
         
         if DISPLAYSTEPS:
-            print "ROOT",root
-            print
-        
+            print "ROOT",root,"\n"
+
         visited = {}
         visited[root] = True
         
         while queue:
             node = queue.popleft()
-            children = self.Graph.AdjacencyList.get(node,None)
-            
-            if children == None:
-                continue
+            children = self.Graph.AdjacencyList[node]
             
             if DISPLAYSTEPS:
                 print "CURRENT NODE: ",node
@@ -97,9 +92,17 @@ class GraphAnalysis:
                     queue.append(childNode)
                     if DISPLAYSTEPS:
                         print "PUSHED: ", childNode
-            if DISPLAYSTEPS:
-                print
 
+    def numberOfNodes(self):
+        return len(self.Graph.AdjacencyList.keys())
+    
+    def numberOfEdges(self):
+        nodeList = self.Graph.AdjacencyList
+        edges = 0
+        for node in nodeList:
+            edgeList = self.Graph.AdjacencyList[node]
+            edges = edges + len(edgeList)
+        return edges
 
 
 if __name__ == "__main__":
@@ -123,6 +126,9 @@ if __name__ == "__main__":
     for root in rootList:
         print root
     print
+
+    print "NUMBER OF ROOTS:", len(rootList)
+    print
     
 
     topoList = analysis.topologicalSort()
@@ -130,3 +136,9 @@ if __name__ == "__main__":
     for node in topoList:
         print node
     print
+
[…]

### 2013-04-30 GraphAnalysis.py
added leafCounts to GraphAnalysis

@@ -97,13 +97,31 @@ class GraphAnalysis:
         return len(self.Graph.AdjacencyList.keys())
     
     def numberOfEdges(self):
-        nodeList = self.Graph.AdjacencyList
         edges = 0
-        for node in nodeList:
+        for node in self.Graph.AdjacencyList:
             edgeList = self.Graph.AdjacencyList[node]
             edges = edges + len(edgeList)
         return edges
 
+    def numberOfLeaves(self):
+        count = 0
+        for node in self.Graph.AdjacencyList:
+            edgeList = self.Graph.AdjacencyList[node]
+            if not edgeList:
+                count += 1
+        return count
+
+    def numberOfNodesEdgesAndLeaves(self):
+        nodes = len(self.Graph.AdjacencyList)
+        edges = 0
+        leafCount = 0
+        for node in self.Graph.AdjacencyList: 
+            edgeList = self.Graph.AdjacencyList[node]
+            if not edgeList:
+                leafCount += 1
+            else:
+                edges += len(edgeList)
+        return (nodes, edges, leafCount)
 
 if __name__ == "__main__":
     parser = DotParser()
@@ -141,4 +159,9 @@ if __name__ == "__main__":
     print "NUMBER OF EDGES AND TOTAL NUMBER OF NODES:"
     print analysis.numberOfEdges(), analysis.numberOfNodes()
     print 
-
+    print "NUMBER OF LEAVES:"
+    print analysis.numberOfLeaves()
+    print
+    print "ALL 3: "
+    print analysis.numberOfNodesEdgesAndLeaves()
+    

### 2013-04-30 GraphAnalysis.py
GraphAnalysis. BFS can now find cycles in your graphs.

@@ -63,7 +63,7 @@ class GraphAnalysis:
         return topoSort
 
 
-    def BFS(self, root):
+    def BFS(self, root, lookForCycles=False):
         DISPLAYSTEPS = False
 
         queue = deque()
@@ -92,6 +92,12 @@ class GraphAnalysis:
                     queue.append(childNode)
                     if DISPLAYSTEPS:
                         print "PUSHED: ", childNode
+                # If we have visited this node, then we have a cycle.
+                elif lookForCycles and childNode not in queue:
+                    #print childNode
+                    return lookForCycles
+        if lookForCycles:
+            return False
 
     def numberOfNodes(self):
         return len(self.Graph.AdjacencyList.keys())
@@ -164,4 +170,6 @@ if __name__ == "__main__":
     print
     print "ALL 3: "
     print analysis.numberOfNodesEdgesAndLeaves()
-    
+    print
+
+    print "GRAPH HAS CYCLES:", analysis.BFS(arbitraryRoot,True)

### 2013-04-30 Graph.py
more nbody stuff

@@ -195,3 +195,7 @@ class Graph:
         y = n1.PosY - n2.PosY
         return sqrt(x**2 + y**2)
 
+    @staticmethod
+    def nodeDistVect(n1, n2):
+        return (abs(n1.PosX-n2.PosX), abs(n1.PosY-n2.PosY))
+

### 2013-04-30 NBodyRepositioner.py

@@ -4,21 +4,42 @@ from sys import floatinfo
 
 bestCopy = None
 minForce = floatinfo.max
+armLength = 3
+springConst = 1
 
-def __calcForce(graph):
-	for 
+def __calcForces(graph):
+	toRet = dict()
+	for n1 in graph.getNodeList():
+		toRet[n1] = list()
+		for n2 in graph.getNodeList():
+			if n1 != n2:
+				(m,n) = Graph.nodeDistVect(n1,n2)
+				d = Graph.nodeDist(n1, n2)
+				f = (armLength**3)/(d**2)
+				toRet[n1].append(((m/d)*f, (n/d)*f))
+				if n2 in graph.AdjacencyList[n1]:
+					toRet[n1].append((m,n))
 
-def __jitter(graph):
-	tHold = graph.copy()
+
+
+
+
+def __jitter(graph, forces):
+	pass
+
+	
 
 
 def reposition(graph):
 	bestCopy = graph.copy()
 
 	for x in xrange(1000):
-		(graph, m) = __jitter(graph).copy()
+		forces = __calcForces(graph)
+		m = sum(forces)
 		if m < minForce:
 			bestCopy = graph.copy()
 			minForce = m
+
+		__jitter(graph, forces)
 
 	return bestCopy

### 2013-04-30 JumanG.py
added a basic JumanG driver. It will eventually make decisions between solvers

@@ -1,0 +1,33 @@
+#!/usr/bin/python
+
+from Utils import *
+from DotParser import *
+import TikzWriter as TW
+
+import RadialDisplay as RD
+
+from sys import argv
+
+
+if __name__ == "__main__":
+    try:
+        infile = argv[1]
+        if len(argv) == 2:
+            outfile = "result.out"
+        else:
+            outfile = argv[2]
+        
+    except IndexError:
+        print
+        print "Usage: ./JumanG.py [inputfile] [outputfile]"
+        print "if not output file is specified, the default output file will be result.out"
+        print
+        exit()
+
+    Parser = DotParser()
+    graph = Parser.readFile(infile)
+
+    RD.radialAssign(graph)
+
+    TW.tikGraph(graph, outfile)
+

### 2013-04-30 JumanG.py
updated JumanG to be more object oriented-y

@@ -8,6 +8,18 @@ import RadialDisplay as RD
 
 from sys import argv
 
+class JumanG:
+    
+    def __init__(self, infile):
+        self.Parser = DotParser()
+        self.Graph = Parser.readFile(infile)
+    
+
+    def outputToTikz(outfile):
+        TW.tikGraph(self.Graph, outfile)
+        
+    def runRadial(self):
+        RD.radialAssign(self.Graph)
 
 if __name__ == "__main__":
     try:
@@ -24,10 +36,7 @@ if __name__ == "__main__":
         print
         exit()
 
-    Parser = DotParser()
-    graph = Parser.readFile(infile)
-
-    RD.radialAssign(graph)
-
-    TW.tikGraph(graph, outfile)
+    juman = JumanG(infile)
+    juman.runRadial()
+    juman.outputToTikz()
 

### 2013-04-30 JumanG.py
removed a misspelling bug. Also changed the runner script to not run pdflatex if JumanG.py fails for some reason

@@ -2,6 +2,7 @@
 
 from Utils import *
 from DotParser import *
+from GraphAnalysis import *
 import TikzWriter as TW
 
 import RadialDisplay as RD
@@ -12,10 +13,10 @@ class JumanG:
     
     def __init__(self, infile):
         self.Parser = DotParser()
-        self.Graph = Parser.readFile(infile)
-    
+        self.Graph = self.Parser.readFile(infile)
+        self.Analysis = GraphAnalysis(self.Graph)
 
-    def outputToTikz(outfile):
+    def outputToTikz(self, outfile):
         TW.tikGraph(self.Graph, outfile)
         
     def runRadial(self):
@@ -38,5 +39,5 @@ if __name__ == "__main__":
 
     juman = JumanG(infile)
     juman.runRadial()
-    juman.outputToTikz()
+    juman.outputToTikz(outfile)
 

### 2013-04-30 BasicDriver.py
PhysX update

@@ -3,6 +3,7 @@ import RadialDisplay as RD
 import TikzWriter as TW
 import sys
 from DotParser import *
+import NBodyRepositioner as NB
 
 argv = sys.argv
 
@@ -22,6 +23,8 @@ DP.readFile(infile)
 graph = DP.Graph
 
 RD.radialAssign(graph)
+
+graph = NB.reposition(graph)
 
 TW.tikGraph(graph, outfile)
 

### 2013-04-30 Graph.py

@@ -19,7 +19,7 @@ class Node:
         node = Node(name, label)
         node.PosX = self.PosX
         node.PosY = self.PosY
-        node.Attributes = copy.deepcopy(self.Attributes)
+        node.Attributes = deepcopy(self.Attributes)
         return node
         
         
@@ -91,7 +91,7 @@ class EdgeType:
         self.Type = typeDict.get(edgeType, None)
         
     def copy(self):
-        theType = copy.deepcopy(self.Type)
+        theType = deepcopy(self.Type)
         edgeType = EdgeType(theType)
         return edgeType
     
@@ -110,7 +110,7 @@ class Graph:
         self.Name = name
         
     def copy(self):
-        name = copy.deepcopy(self.Name)
+        name = deepcopy(self.Name)
         graph = Graph(name)
         for node in self.AdjacencyList:
             copiedNode = node.copy()
@@ -120,7 +120,7 @@ class Graph:
             for (node2,Type) in edgeList:
                 copiedNode2 = node2.copy()
                 copiedType = Type.copy()
-                graph.Adjacencylist[copiedNode].append((copiedNode2,copiedType))
+                graph.AdjacencyList[copiedNode].append((copiedNode2,copiedType))
         return graph
 
 
@@ -197,5 +197,5 @@ class Graph:
 
     @staticmethod
     def nodeDistVect(n1, n2):
-        return (abs(n1.PosX-n2.PosX), abs(n1.PosY-n2.PosY))
+        return (n1.PosX-n2.PosX, n1.PosY-n2.PosY)
 

### 2013-04-30 NBodyRepositioner.py

@@ -1,9 +1,7 @@
 from Graph import *
 from Utils import *
-from sys import floatinfo
+from sys import float_info
 
-bestCopy = None
-minForce = floatinfo.max
 armLength = 3
 springConst = 1
 
@@ -15,27 +13,50 @@ def __calcForces(graph):
 			if n1 != n2:
 				(m,n) = Graph.nodeDistVect(n1,n2)
 				d = Graph.nodeDist(n1, n2)
-				f = (armLength**3)/(d**2)
-				toRet[n1].append(((m/d)*f, (n/d)*f))
-				if n2 in graph.AdjacencyList[n1]:
-					toRet[n1].append((m,n))
+				f = (armLength)/(d**2)
+				toRet[n1].append((-(m/d)*f, -(n/d)*f))
+				for (n3, l) in graph.AdjacencyList[n1]:
+					if n2 == n3:
+						toRet[n1].append((m,n))
+
+	return toRet
 
 
 
 
 
 def __jitter(graph, forces):
-	pass
+	for n in forces.keys():
+		xTot = 0
+		yTot = 0
+		for (x, y) in forces[n]:
+			xTot += x
+			yTot += y 
+		n.PosX -= xTot * .01
+		n.PosY -= yTot * .01
 
 	
 
 
 def reposition(graph):
 	bestCopy = graph.copy()
+	minForce = float_info.max
 
 	for x in xrange(1000):
 		forces = __calcForces(graph)
-		m = sum(forces)
+		m = 0
+		for n in forces.keys():
+			xTot = 0
+			yTot = 0
+			for (x1, y1) in forces[n]:
+				xTot += x1
+				yTot += y1
+				
+			# print n, xTot, yTot
+
+			m += sqrt(xTot**2 + yTot**2)
+		# print
+
 		if m < minForce:
 			bestCopy = graph.copy()
 			minForce = m

### 2013-04-30 JumanG.py
moved the solvers to a seperate directory. Also changed the import statements of JumanG.py to reflect this

@@ -5,7 +5,8 @@ from DotParser import *
 from GraphAnalysis import *
 import TikzWriter as TW
 
-import RadialDisplay as RD
+import Solvers
+import Solvers.RadialDisplay as RD
 
 from sys import argv
 

### 2013-04-30 Solvers/RadialDisplay.py
I should also add the blank __init__.py file as well

@@ -1,3 +1,4 @@
+#!/usr/bin/python
 from Graph import *
 from Utils import *
 from GraphAnalysis import *

### 2013-04-30 BasicDriver.py
Also fixed basic driver as well. Just for Mango.

@@ -1,9 +1,12 @@
+#!/usr/bin/python
+
 from Graph import *
-import RadialDisplay as RD
+
+import Solvers.RadialDisplay as RD
 import TikzWriter as TW
 import sys
 from DotParser import *
-import NBodyRepositioner as NB
+import Solvers.NBodyRepositioner as NB
 
 argv = sys.argv
 

### 2013-05-01 DotParser.py
added name and type parsing into DotParser.py

@@ -5,7 +5,6 @@ from Graph import *
 
 
 class DotParser:
-
    def __init__(self):
       self.Graph = Graph()
 
@@ -33,6 +32,10 @@ class DotParser:
          if braceStack == 0:
             break
          outerClose = outerClose + 1
+
+      
+      header = FILE[:outer-1]
+      self.readNameAndType(header)
             
 
       # From within the outer { } braces, we parse the graph
@@ -99,6 +102,12 @@ class DotParser:
       for n in self.Graph.AdjacencyList:
          self.Graph.addNode(n)
       return self.Graph
+
+   def readNameAndType(self, header):
+      header = header.split()
+      self.Graph.Type = header[0]
+      self.Graph.Name = header[1]
+
 
 
 if __name__ ==  "__main__":

### 2013-05-01 Graph.py

@@ -108,7 +108,8 @@ class Graph:
         #self.NodeList = {}
         self.AdjacencyList = {}
         self.Name = name
-        
+        self.Type = None
+
     def copy(self):
         name = deepcopy(self.Name)
         graph = Graph(name)
@@ -165,7 +166,10 @@ class Graph:
         result = "Graph "
         
         if self.Name != None:
-            result = result + self.Name
+            result = result + self.Name + " "
+
+        if self.Type != None:
+            result = result + "(" + self.Type + ")"
 
         result = result + "\n"
         result = result + "Nodes: \n"

### 2013-05-01 BasicDriver.py
k5 and updates

@@ -20,6 +20,7 @@ else:
 	infile = argv[1]
 	outfile = argv[2]
 
+directed = False
 DP = DotParser()
 
 DP.readFile(infile)

### 2013-05-01 Solvers/NBodyRepositioner.py

@@ -13,7 +13,7 @@ def __calcForces(graph):
 			if n1 != n2:
 				(m,n) = Graph.nodeDistVect(n1,n2)
 				d = Graph.nodeDist(n1, n2)
-				f = (armLength)/(d**2)
+				f = (armLength**3)/(d**2)
 				toRet[n1].append((-(m/d)*f, -(n/d)*f))
 				for (n3, l) in graph.AdjacencyList[n1]:
 					if n2 == n3:

### 2013-05-01 Solvers/RadialDisplay.py

@@ -10,7 +10,7 @@ visited = list()
 
 # @Graph: graph to be sorted
 # @Sink: If the sink should be the center, rather than the source
-def __recRadial(graph, root, degrees, start, layer):
+def __recRadial(graph, root, degrees, start, layer, d):
 
 	children = graph.AdjacencyList[root]
 
@@ -23,7 +23,8 @@ def __recRadial(graph, root, degrees, start, layer):
 	for (c, t) in children:
 		if c in visited:
 			continue
-		visited.append(c)
+		if not d:
+			visited.append(c)
 		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
 		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
 
@@ -35,7 +36,7 @@ def __recRadial(graph, root, degrees, start, layer):
 		c.PosX = x
 		c.PosY = y
 
-		__recRadial(graph, c, subDeg, currentDegrees, layer+1)
+		__recRadial(graph, c, subDeg, currentDegrees, layer+1, d)
 		currentDegrees += subDeg
 
 
@@ -58,7 +59,7 @@ def radialAssign(graph, sink = False):
 
 	# TODO: Add support for multiple roots
 
-	__recRadial(graph, gSorted[0], 360, 0, 1)
+	__recRadial(graph, gSorted[0], 360, 0, 1, False)
 	# __recRadial(graph, root, 360,0,1)
 
 

### 2013-05-01 DotParser.py
changed the internal representation of graph types to be an integer. 0 for undirected and 1 for directed

@@ -105,7 +105,11 @@ class DotParser:
 
    def readNameAndType(self, header):
       header = header.split()
-      self.Graph.Type = header[0]
+      
+      graphType = header[0]
+      
+      self.Graph.Type = {"digraph":1, "graph":0}.get(graphType, 0)
+      
       self.Graph.Name = header[1]
 
 

### 2013-05-01 Graph.py

@@ -108,6 +108,9 @@ class Graph:
         #self.NodeList = {}
         self.AdjacencyList = {}
         self.Name = name
+
+        # 0 is an undirected graph.
+        # 1 is a directed graph.
         self.Type = None
 
     def copy(self):
@@ -169,7 +172,7 @@ class Graph:
             result = result + self.Name + " "
 
         if self.Type != None:
-            result = result + "(" + self.Type + ")"
+            result = result + "(" + {0:"Undirected Graph", 1:"Directed Graph"}[self.Type] + ")"
 
         result = result + "\n"
         result = result + "Nodes: \n"

### 2013-05-01 BasicDriver.py
stuff

@@ -25,9 +25,9 @@ DP = DotParser()
 
 DP.readFile(infile)
 graph = DP.Graph
-
-RD.radialAssign(graph)
-
+# print graph
+graph = RD.radialAssign(graph)
+# print graph
 graph = NB.reposition(graph)
 
 TW.tikGraph(graph, outfile)

### 2013-05-01 Graph.py

@@ -164,6 +164,12 @@ class Graph:
             node2 = self.AdjacencyList.keys()[index]
             self.AdjacencyList[e.Node1].append((node2, e.Type))
 
+    def getNumEdges(self):
+        out = 0
+        for n in self.AdjacencyList.keys():
+            out += len(self.AdjacencyList[n])
+        return out;
+
 
     def __str__(self):
         result = "Graph "

### 2013-05-01 Solvers/NBodyRepositioner.py

@@ -2,10 +2,11 @@ from Graph import *
 from Utils import *
 from sys import float_info
 
-armLength = 3
 springConst = 1
+armLength = 0
 
 def __calcForces(graph):
+	# print armLength
 	toRet = dict()
 	for n1 in graph.getNodeList():
 		toRet[n1] = list()
@@ -13,6 +14,8 @@ def __calcForces(graph):
 			if n1 != n2:
 				(m,n) = Graph.nodeDistVect(n1,n2)
 				d = Graph.nodeDist(n1, n2)
+				if d ==0:
+					d = 1
 				f = (armLength**3)/(d**2)
 				toRet[n1].append((-(m/d)*f, -(n/d)*f))
 				for (n3, l) in graph.AdjacencyList[n1]:
@@ -39,6 +42,7 @@ def __jitter(graph, forces):
 
 
 def reposition(graph):
+	armLength = graph.getNumEdges() // 4 + 1
 	bestCopy = graph.copy()
 	minForce = float_info.max
 
@@ -61,6 +65,6 @@ def reposition(graph):
 			bestCopy = graph.copy()
 			minForce = m
 
-		__jitter(graph, forces)
+		__jitter(graph.copy(), forces)
 
 	return bestCopy

### 2013-05-01 Solvers/RadialDisplay.py

@@ -41,8 +41,10 @@ def __recRadial(graph, root, degrees, start, layer, d):
 
 
 
-def radialAssign(graph, sink = False):
+def radialAssign(g, sink = False):
 
+	graph = g.copy()
+	# print graph
 	gSorted = list()
 	visited = list()
 
@@ -56,10 +58,13 @@ def radialAssign(graph, sink = False):
 	gSorted[0].PosY=0
 	# root.PosX=0
 	# root.PosY=0
+	d = False
+	if graph.Type == 1 :
+		d = True
 
 	# TODO: Add support for multiple roots
 
-	__recRadial(graph, gSorted[0], 360, 0, 1, False)
-	# __recRadial(graph, root, 360,0,1)
-
+	__recRadial(graph, gSorted[0], 360, 0, 1, d)
+	print graph
+	return graph
 

### 2013-05-01 Solvers/NBodyRepositioner.py
Cool changes for cool people

@@ -6,6 +6,12 @@ springConst = 1
 armLength = 0
 
 def __calcForces(graph):
+	global armLength
+	# mult = 1
+	if graph.Type ==1:
+		# mult = 16
+		armLength /=2
+
 
 	toRet = dict()
 	for n1 in graph.getNodeList():

### 2013-05-01 Solvers/NBodyRepositioner.py
fix

@@ -12,11 +12,6 @@ def __calcForces(graph):
 		# mult = 16
 		armLength /=2
 
-<<<<<<< HEAD
-=======
-        #print armLength
->>>>>>> 4c3cf51fb0a151f410a8e0324a36432a3282162d
-
 	toRet = dict()
 	for n1 in graph.getNodeList():
 		toRet[n1] = list()

### 2013-05-02 Solvers/NBodyRepositioner.py
added random jitters to the initialization step of the NBody simulator. I think technically you are supposed to add random jitters before starting the NBody simulator.

@@ -2,6 +2,8 @@ from Graph import *
 from Utils import *
 from sys import float_info
 
+from random import uniform
+
 springConst = 1
 armLength = 0
 
@@ -51,6 +53,12 @@ def reposition(graph):
 	armLength = graph.getNumEdges() // 4 + 1
 	bestCopy = graph.copy()
 	minForce = float_info.max
+
+        #Added random jitters to all the initial starting points for the nodes
+        for node in graph.AdjacencyList:
+                node.PosX += uniform(-1,1)
+                node.PosY += uniform(-1,1)
+
 
 	for x in xrange(1000):
 		forces = __calcForces(graph)

### 2013-05-02 TikzWriter.py
stripped out the underscores when outputting to Tikz. So that we can run ethane.dot

@@ -13,14 +13,22 @@ def tikGraph(graph, l = None):
 	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
 
 	for n in graph.getNodeList():
-		output+="\t\\node ("+n.Name+") at ("+"{0:.2f}".format(n.PosX)+", "+"{0:.2f}".format(n.PosY)+") {"+n.Name+"};\n"
+                cleanedName = n.Name
+                cleanedName = cleanedName.replace("_","")
+                
+		output+="\t\\node ("+cleanedName+") at ("+"{0:.2f}".format(n.PosX)+", "+"{0:.2f}".format(n.PosY)+") {"+cleanedName+"};\n"
 
 	for n1 in graph.getNodeList():
 		for (n2, t) in graph.AdjacencyList[n1]:
+                        cleanedN = n1.Name
+                        cleanedN = cleanedN.replace("_", "")
+                        cleanedN2 = n2.Name
+                        cleanedN2 = cleanedN2.replace("_","")
+
 			if t.Type==1:
-				output+="\t\\draw [->] ("+n1.Name+")--("+n2.Name+");\n"
+				output+="\t\\draw [->] ("+cleanedN+")--("+cleanedN2+");\n"
 			else:
-				output+="\t\\draw [-] ("+n1.Name+")--("+n2.Name+");\n"
+				output+="\t\\draw [-] ("+cleanedN+")--("+cleanedN2+");\n"
 
 
 	output += "\\end{tikzpicture}\n"

### 2013-05-02 GraphAnalysis.py
played around with NBodySimulations and TikzWriter. Didn't make much progress

@@ -8,8 +8,9 @@ from DotParser import *
 class GraphAnalysis:
     def __init__(self, graph):
         self.Graph = graph
-        self.RootNode = None
-        self.DependencyTable = self.buildDependencyTable(self.Graph)
+        #self.RootNode = None
+        #self.DependencyTable = self.buildDependencyTable(self.Graph)
+        self.DependencyTable = None
 
 
     def buildDependencyTable(self, graph):
@@ -23,6 +24,9 @@ class GraphAnalysis:
         return dependencyTable
 
     def printDependencyTable(self):
+        if self.DependencyTable == None:
+            self.buildDependencyTable(self.Graph)
+
         print "dependency Table: "
         string = ""
         for node in self.DependencyTable:
@@ -36,6 +40,9 @@ class GraphAnalysis:
         print string
 
     def getRootNodes(self):
+        if self.DependencyTable == None:
+            self.DependencyTable = self.buildDependencyTable(self.Graph)
+
         rootList = []
         for node in self.Graph.getNodeList():
             if node not in self.DependencyTable:
@@ -44,7 +51,7 @@ class GraphAnalysis:
 
 
     def topologicalSort(self):
-        #dependencyTable = self.buildDependencyTable(self.Graph)
+        dependencyTable = self.buildDependencyTable(self.Graph)
         queue = self.getRootNodes()
         topoSort = []
 
@@ -59,7 +66,7 @@ class GraphAnalysis:
                     self.DependencyTable.get(adjacency).remove(n)
                     if not self.DependencyTable.get(adjacency):
                         queue.append(adjacency)
-        self.DependencyTable = self.buildDependencyTable(self.Graph)
+        #self.DependencyTable = self.buildDependencyTable(self.Graph)
         return topoSort
 
 

### 2013-05-02 JumanG.py

@@ -1,12 +1,14 @@
 #!/usr/bin/python
 
 from Utils import *
+from Graph import *
 from DotParser import *
 from GraphAnalysis import *
 import TikzWriter as TW
 
 import Solvers
 import Solvers.RadialDisplay as RD
+import Solvers.NBodyRepositioner as NB
 
 from sys import argv
 
@@ -17,11 +19,14 @@ class JumanG:
         self.Graph = self.Parser.readFile(infile)
         self.Analysis = GraphAnalysis(self.Graph)
 
-    def outputToTikz(self, outfile):
-        TW.tikGraph(self.Graph, outfile)
+    def outputToTikz(self, graph, outfile):
+        TW.tikGraph(graph, outfile)
         
     def runRadial(self):
-        RD.radialAssign(self.Graph)
+        return RD.radialAssign(self.Graph)
+
+    def runNBody(self):
+        return NB.reposition(self.runRadial())
 
 if __name__ == "__main__":
     try:
@@ -39,6 +44,12 @@ if __name__ == "__main__":
         exit()
 
     juman = JumanG(infile)
-    juman.runRadial()
-    juman.outputToTikz(outfile)
+    graph = juman.runRadial()
+
+    print graph
+    graph = juman.runNBody()
+    
+    print graph
+
+    juman.outputToTikz(graph, outfile)
 

### 2013-05-02 Solvers/NBodyRepositioner.py

@@ -1,10 +1,13 @@
 from Graph import *
+from GraphAnalysis import *
+
 from Utils import *
 from sys import float_info
 
 from random import uniform
 
-springConst = 1
+#springConst = 1
+k = 1
 armLength = 0
 
 def __calcForces(graph):
@@ -23,8 +26,12 @@ def __calcForces(graph):
 				d = Graph.nodeDist(n1, n2)
 				if d ==0:
 					d = 1
-				f = (armLength**3)/(d**2)
-				toRet[n1].append((-(m/d)*f, -(n/d)*f))
+
+                                f = (armLength**3)/(d**2)
+                                #f = (d**2/k - k**2/d)
+                                
+                                
+                                toRet[n1].append((-(m/d)*f, -(n/d)*f))
 				for (n3, l) in graph.AdjacencyList[n1]:
 					if n2 == n3:
 						toRet[n1].append((m,n))
@@ -49,6 +56,10 @@ def __jitter(graph, forces):
 
 
 def reposition(graph):
+        #analysis = GraphAnalysis(graph)
+        #k = sqrt(100/analysis.numberOfEdges())
+
+
 	global armLength
 	armLength = graph.getNumEdges() // 4 + 1
 	bestCopy = graph.copy()
@@ -58,7 +69,7 @@ def reposition(graph):
         for node in graph.AdjacencyList:
                 node.PosX += uniform(-1,1)
                 node.PosY += uniform(-1,1)
-
+        
 
 	for x in xrange(1000):
 		forces = __calcForces(graph)
@@ -71,9 +82,10 @@ def reposition(graph):
 				yTot += y1
 				
 			# print n, xTot, yTot
-
+                        
 			m += sqrt(xTot**2 + yTot**2)
-		# print
+                        #print m
+                # print
 
 		if m < minForce:
 			bestCopy = graph.copy()

### 2013-05-02 TikzWriter.py

@@ -1,21 +1,34 @@
 #!/usr/bin/python
 from Graph import *
+from GraphAnalysis import *
+from math import *
 
 def tikGraph(graph, l = None):
+        analysis = GraphAnalysis(graph)
+        n = analysis.numberOfNodes()
+        #scaleFactor = 1 / log(n)
+        scaleFactor = 0.9
+        #print n, scaleFactor
+        #exit()
+        
 	output = ""
 	output += "% Tik output from JumanG\n"
-	output += "\\documentclass{article}\n"
+	output += "\\documentclass[class=minimal,border=0pt]{article}\n"
 	output += "\\usepackage{tikz}\n"
 	output += "\\pagestyle{empty}\n"
 	output += "\\usepackage{verbatim}\n"
 	output += "\\begin{document}\n"
-	output += "\\begin{tikzpicture}[scale=.9, transform shape]\n"
+
+        #output += "\\resizebox{100}{100}{\n"
+	output += "\\begin{tikzpicture}[scale="+"{0:.2f}".format(scaleFactor)+", transform shape]\n"
 	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
 
 	for n in graph.getNodeList():
                 cleanedName = n.Name
                 cleanedName = cleanedName.replace("_","")
-                
+                x = n.PosX
+                y = n.PosY
+
 		output+="\t\\node ("+cleanedName+") at ("+"{0:.2f}".format(n.PosX)+", "+"{0:.2f}".format(n.PosY)+") {"+cleanedName+"};\n"
 
 	for n1 in graph.getNodeList():
@@ -32,6 +45,8 @@ def tikGraph(graph, l = None):
 
 
 	output += "\\end{tikzpicture}\n"
+        #output += "}\n"
+        
 	output += "\\end{document}\n"
 
 	if l:

### 2013-05-02 doc/paper.tex
wrote out some more of the outline of the writeup

% Juneki Hong and Michael Tango
% Declarative Methods
% Professor Eisner
% May 3, 2013

\documentclass{article}
\author{Juneki Hong and Michael Tango}
\title{Declarative Methods Term Project: \\ JumanG}
%\usepackage[ampersand]{easylist}

\begin{document}

\maketitle
\newpage

\section{Introduction}

\section{Problem we decided to solve}

\section{How we solved it}

Encoder

Solver

Decoder

\subsection{The Encoder}
The Dot Parser

\subsection{The Solvers}

\subsubsection{Springs Solver}
citation for the springs\cite{springs}

\subsection{The Decoder}

\section{The results}

\section{Experimental Comparison}

\section{Future Work}

\bibliographystyle{plain}
\bibliography{citations}

\end{document}

### 2013-05-02 doc/clean.sh

@@ -1,0 +1,2 @@
+rm *.aux *.log *.bbl *.blg
+rm *.dvi

### 2013-05-02 doc/runScript.sh

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+
+rm *.aux *.log *~
+rm *.dvi
+
+latex $1
+bibtex ${1%.*}.aux
+latex $1
+pdflatex $1
+
+./clean.sh
+#rm *.dvi

### 2013-05-03 BasicDriver.py
NBODy fix

@@ -7,6 +7,7 @@ import TikzWriter as TW
 import sys
 from DotParser import *
 import Solvers.NBodyRepositioner as NB
+import Solvers.TopDownSolver as TD
 
 argv = sys.argv
 
@@ -27,9 +28,10 @@ DP.readFile(infile)
 graph = DP.Graph
 # print graph
 graph = RD.radialAssign(graph)
-print graph
-graph = NB.reposition(graph)
-print graph
+# print graph
+# print graph
+# graph = TD.arrange(graph)
+graph = NB.reposition(graph, False)
 
 TW.tikGraph(graph, outfile)
 

### 2013-05-03 JumanG.py

@@ -26,7 +26,7 @@ class JumanG:
         return RD.radialAssign(self.Graph)
 
     def runNBody(self):
-        return NB.reposition(self.runRadial())
+        return NB.reposition(self.runRadial(), false)
 
 if __name__ == "__main__":
     try:

### 2013-05-03 Solvers/NBodyRepositioner.py

@@ -16,7 +16,10 @@ def __calcForces(graph):
 	if graph.Type ==1:
 		# mult = 16
 		armLength /=2
+	if armLength<2:
+		armLength = 2
 
+	# print armLength
 	toRet = dict()
 	for n1 in graph.getNodeList():
 		toRet[n1] = list()
@@ -27,11 +30,11 @@ def __calcForces(graph):
 				if d ==0:
 					d = 1
 
-                                f = (armLength**3)/(d**2)
-                                #f = (d**2/k - k**2/d)
-                                
-                                
-                                toRet[n1].append((-(m/d)*f, -(n/d)*f))
+				f = (armLength**3)/(d**2)
+				#f = (d**2/k - k**2/d)
+				
+				
+				toRet[n1].append((-(m/d)*f, -(n/d)*f))
 				for (n3, l) in graph.AdjacencyList[n1]:
 					if n2 == n3:
 						toRet[n1].append((m,n))
@@ -55,21 +58,24 @@ def __jitter(graph, forces):
 	
 
 
-def reposition(graph):
-        #analysis = GraphAnalysis(graph)
-        #k = sqrt(100/analysis.numberOfEdges())
+def reposition(graph, reposition = True):
+	#analysis = GraphAnalysis(graph)
+	#k = sqrt(100/analysis.numberOfEdges())
 
 
 	global armLength
 	armLength = graph.getNumEdges() // 4 + 1
+	# print graph.getNumEdges()
+
 	bestCopy = graph.copy()
 	minForce = float_info.max
 
-        #Added random jitters to all the initial starting points for the nodes
-        for node in graph.AdjacencyList:
-                node.PosX += uniform(-1,1)
-                node.PosY += uniform(-1,1)
-        
+	#Added random jitters to all the initial starting points for the nodes
+	if reposition:
+		for node in graph.AdjacencyList:
+			node.PosX += uniform(-1,1)
+			node.PosY += uniform(-1,1)
+		
 
 	for x in xrange(1000):
 		forces = __calcForces(graph)
@@ -82,10 +88,10 @@ def reposition(graph):
 				yTot += y1
 				
 			# print n, xTot, yTot
-                        
+						
 			m += sqrt(xTot**2 + yTot**2)
-                        #print m
-                # print
+						#print m
+				# print
 
 		if m < minForce:
 			bestCopy = graph.copy()

### 2013-05-03 Solvers/RadialDisplay.py

@@ -22,8 +22,8 @@ def __recRadial(graph, root, degrees, start, layer, d):
 	for (c, t) in children:
 		if c in visited:
 			continue
-		if not d:
-			visited.append(c)
+		# if not d:
+		visited.append(c)
 		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
 		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
 
@@ -34,9 +34,10 @@ def __recRadial(graph, root, degrees, start, layer, d):
 
 		c.PosX = x
 		c.PosY = y
-
-		__recRadial(graph, c, subDeg, currentDegrees, layer+1, d)
 		currentDegrees += subDeg
+
+	for(c, t) in children:
+		__recRadial(graph, c, subDeg, currentDegrees, layer+1, d)
 
 
 

### 2013-05-03 Solvers/TopDownSolver.py

@@ -1,0 +1,47 @@
+from Graph import *
+from GraphAnalysis import *
+
+armLength = 3
+toAdjust = list()
+
+def layout(nodes, maximum):
+	for y in xrange(len(nodes)):
+		l = nodes [y]
+		for x in xrange(len(l)):
+			xMod = maximum/len(l) * armLength
+			l[x].PosY = armLength*y
+			if len(l) % 2 == 0:
+				midpoint = len(l)/2
+				l[x].PosX = ((x-midpoint)*xMod) -1.5
+			else:
+				midpoint = (len(l)+1)/2
+				l[x].PosX = (x - midpoint)* xMod
+
+
+
+def arrange(g):
+	global toAdjust
+	
+	graph = g.copy()
+	GA = GraphAnalysis(graph)
+	nodepairs = GA.topologicalSort(True)
+	most = 0
+	nodes = list()
+	nodes.append(list())
+
+	current = 0
+	count = 0
+
+	for (n, l) in nodepairs:
+		if l>current:
+			current+=1
+			if count > most:
+				most = count
+			count = 0
+			nodes.append(list())
+		nodes[l].append(n)
+
+	layout(nodes, most)
+	return graph
+
+

### 2013-05-03 TikzWriter.py

@@ -21,7 +21,7 @@ def tikGraph(graph, l = None):
 
         #output += "\\resizebox{100}{100}{\n"
 	output += "\\begin{tikzpicture}[scale="+"{0:.2f}".format(scaleFactor)+", transform shape]\n"
-	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 2cm]\n"
+	output += "\t\\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]\n"
 
 	for n in graph.getNodeList():
                 cleanedName = n.Name

### 2013-05-03 BasicDriver.py
merged BasicDriver.py. Merge happened because I commented out some lines during our ACM presentation.

@@ -29,9 +29,9 @@ graph = DP.Graph
 # print graph
 graph = RD.radialAssign(graph)
 # print graph
-# print graph
 # graph = TD.arrange(graph)
 graph = NB.reposition(graph, False)
+
 
 TW.tikGraph(graph, outfile)
 

### 2013-05-03 GraphAnalysis.py

@@ -12,7 +12,6 @@ class GraphAnalysis:
         #self.DependencyTable = self.buildDependencyTable(self.Graph)
         self.DependencyTable = None
 
-
     def buildDependencyTable(self, graph):
         dependencyTable = {}
         
@@ -49,9 +48,9 @@ class GraphAnalysis:
                 rootList.append(node)
         return rootList
 
-
     def topologicalSort(self, getLevel=False):
         dependencyTable = self.buildDependencyTable(self.Graph)
+        topoSort = []
         queue = deque()
         if getLevel:
             for n in self.getRootNodes():
@@ -60,10 +59,6 @@ class GraphAnalysis:
             for n in self.getRootNodes():
                 queue.append(n)
 
-        #print queue
-
-        topoSort = []
-
         while queue:
             if getLevel:
                 (n,level) = queue.popleft()
@@ -71,26 +66,22 @@ class GraphAnalysis:
             else:
                 n = queue.popleft()
                 topoSort.append(n)
-            #print n.Name
 
             adjacencies = self.Graph.AdjacencyList.get(n,None)
-            #print "_______", adjacencies
             if not adjacencies == None: 
                 for (adjacency,edgeType) in adjacencies:
-                    #print adjacencies, "|", adjacency, " | ", n
                     dependencyTable.get(adjacency).remove(n)
                     if not dependencyTable.get(adjacency):
                         if getLevel:
                             queue.append((adjacency,level+1))
                         else:
                             queue.append(adjacency)
-        
-            #print queue
         return topoSort
 
 
     def BFS(self, root, lookForCycles=False):
         DISPLAYSTEPS = False
+        cycleCount= 0
 
         queue = deque()
         queue.append(root)
@@ -120,10 +111,11 @@ class GraphAnalysis:
                         print "PUSHED: ", childNode
                 # If we have visited this node, then we have a cycle.
                 elif lookForCycles and childNode not in queue:
-                    #print childNode
-                    return lookForCycles
+                    print childNode
+                    cycleCount += 1
+                    #return lookForCycles
         if lookForCycles:
-            return False
+            return cycleCount
 
     def numberOfNodes(self):
         return len(self.Graph.AdjacencyList.keys())
@@ -205,5 +197,6 @@ if __name__ == "__main__":
     print
 
     print "GRAPH HAS CYCLES:", analysis.BFS(arbitraryRoot,True)
+    print
 
-    
+    print analysis.BFS(arbitraryRoot,True)

### 2013-05-03 JumanG.py
here is the current state of the project

@@ -26,7 +26,7 @@ class JumanG:
         return RD.radialAssign(self.Graph)
 
     def runNBody(self):
-        return NB.reposition(self.runRadial(), false)
+        return NB.reposition(self.runRadial(),False)
 
 if __name__ == "__main__":
     try:
@@ -44,11 +44,10 @@ if __name__ == "__main__":
         exit()
 
     juman = JumanG(infile)
-    graph = juman.runRadial()
 
+    graph = juman.runRadial()
     print graph
     graph = juman.runNBody()
-    
     print graph
 
     juman.outputToTikz(graph, outfile)

### 2013-05-03 BasicDriver.py
dumb

@@ -27,12 +27,12 @@ DP = DotParser()
 DP.readFile(infile)
 graph = DP.Graph
 # print graph
-graph = RD.radialAssign(graph)
+graph3 = RD.radialAssign(graph)
 # print graph
 # print graph
 # graph = TD.arrange(graph)
-graph = NB.reposition(graph, False)
+graph2 = NB.reposition(graph3, False)
 
-TW.tikGraph(graph, outfile)
+TW.tikGraph(graph2, outfile)
 
 

### 2013-05-03 Solvers/NBodyRepositioner.py

@@ -58,7 +58,8 @@ def __jitter(graph, forces):
 	
 
 
-def reposition(graph, reposition = True):
+def reposition(g, reposition = True):
+	graph= g.copy()
 	#analysis = GraphAnalysis(graph)
 	#k = sqrt(100/analysis.numberOfEdges())
 

### 2013-05-03 Solvers/TopDownSolver.py
made a fix or two to TopDownSolver.py

@@ -1,22 +1,24 @@
 from Graph import *
 from GraphAnalysis import *
 
+from math import log
+
 armLength = 3
 toAdjust = list()
 
 def layout(nodes, maximum):
 	for y in xrange(len(nodes)):
 		l = nodes [y]
+                count = 0
 		for x in xrange(len(l)):
 			xMod = maximum/len(l) * armLength
-			l[x].PosY = armLength*y
-			if len(l) % 2 == 0:
+			l[x].PosY = -armLength*y
+                        if len(l) % 2 == 0:
 				midpoint = len(l)/2
-				l[x].PosX = ((x-midpoint)*xMod) -1.5
+				l[x].PosX = ((x-midpoint)*xMod) -1.5 +armLength*x
 			else:
 				midpoint = (len(l)+1)/2
-				l[x].PosX = (x - midpoint)* xMod
-
+				l[x].PosX = (x - midpoint)* xMod +armLength*x
 
 
 def arrange(g):
@@ -25,6 +27,9 @@ def arrange(g):
 	graph = g.copy()
 	GA = GraphAnalysis(graph)
 	nodepairs = GA.topologicalSort(True)
+        (_,lengthOfGraph) = nodepairs[-1]
+        armLength = 3 / log(lengthOfGraph)
+
 	most = 0
 	nodes = list()
 	nodes.append(list())

### 2013-05-03 JumanG.py
FIXES FOR MIXES

@@ -46,9 +46,11 @@ if __name__ == "__main__":
     juman = JumanG(infile)
 
     graph = juman.runRadial()
-    print graph
+    # print graph
+    # graph = juman.runRadial()
+    # print graph
     graph = juman.runNBody()
-    print graph
+    # print graph
 
     juman.outputToTikz(graph, outfile)
 

### 2013-05-03 Solvers/NBodyRepositioner.py

@@ -59,7 +59,7 @@ def __jitter(graph, forces):
 
 
 def reposition(g, reposition = True):
-	graph= g.copy()
+	graph = g.copy()
 	#analysis = GraphAnalysis(graph)
 	#k = sqrt(100/analysis.numberOfEdges())
 

### 2013-05-03 Solvers/RadialDisplay.py

@@ -42,6 +42,8 @@ def __recRadial(graph, root, degrees, start, layer, d):
 
 
 def radialAssign(g, sink = False):
+	global visited
+	visited = list()
 
 	graph = g.copy()
 	# graph = g

### 2013-05-03 JumanG.py
automerged JumanG.py

@@ -9,6 +9,7 @@ import TikzWriter as TW
 import Solvers
 import Solvers.RadialDisplay as RD
 import Solvers.NBodyRepositioner as NB
+import Solvers.TopDownSolver as TD
 
 from sys import argv
 
@@ -27,6 +28,9 @@ class JumanG:
 
     def runNBody(self):
         return NB.reposition(self.runRadial(),False)
+
+    def runTopDown(self):
+        return TD.arrange(self.Graph)
 
 if __name__ == "__main__":
     try:
@@ -51,6 +55,9 @@ if __name__ == "__main__":
     # print graph
     graph = juman.runNBody()
     # print graph
+
+    graph = juman.runTopDown()
+    print graph
 
     juman.outputToTikz(graph, outfile)
 

### 2013-05-03 Graph.py
finished the implementation for TopDownSolver

@@ -111,7 +111,6 @@ class EdgeType:
 
 class Graph:
     def __init__(self, name = None):
-        #self.NodeList = {}
         self.AdjacencyList = {}
         self.Name = name
 
@@ -137,6 +136,17 @@ class Graph:
                 graph.addEdge(copiedEdge)
                 #graph.AdjacencyList[copiedNode].append((copiedNode2,copiedType))
         return graph
+
+
+    # Checks if node1 is adjacent to node2. In that order.
+    def isAdjacent(self,node1, node2):
+        edgeList = self.AdjacencyList.get(node1,None)
+        if edgeList == None:
+            return False
+        for (n2,edgeType) in edgeList:
+            if n2 == node2:
+                return True
+        return False
 
 
     def getNodeList(self):
@@ -243,3 +253,6 @@ if __name__ == "__main__":
 
     print graph
     print graph2
+
+    print "Node1 is adjacent to node2:"
+    print graph.isAdjacent(n1,n2)

### 2013-05-03 doc/paper.tex
cool beans

@@
 \documentclass{article}
+\usepackage{acl2012}
+\usepackage{times}
+\usepackage{latexsym}
+\usepackage{amsmath}
+\usepackage{multirow}
+\usepackage{url}
+\setlength\titlebox{6.5cm}    % Expanding the titlebox
+
+\title{Declarative Methods Term Project: \\ JumanG}
 \author{Juneki Hong and Michael Tango}
-\title{Declarative Methods Term Project: \\ JumanG}
+
 %\usepackage[ampersand]{easylist}
 
+\date{}
 \begin{document}
+\maketitle
 
-\maketitle
-\newpage
+\begin{abstract}
+We attempted to display a description of a graph in a nicely formatted 
+We approached this problem using a variety of different algorithms
+\end{abstract}
 
@@
 
-\section{Problem we decided to solve}
+\section{Graph Drawing}
 
-\section{How we solved it}
+\section{Declarative Pipeline}
 
-Encoder
-
-Solver
-
-Decoder
+We had an Encoder, Solver, and a Decoder
 
@@
 
+\subsubsection{Radial Solver}
+Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
+Rarely, however, has it been used to display graphs. We implemented a solver that lays out a graph radially, from the center out.
+These
+
 \subsubsection{Springs Solver}
@@
 \subsection{The Decoder}
-
-\section{The results}
+Tikz
 
@@
 
+\section{Conclusions}
+
 \bibliographystyle{plain}

### 2013-05-03 BasicDriver.py

@@ -27,10 +27,10 @@ DP = DotParser()
 DP.readFile(infile)
 graph = DP.Graph
 # print graph
-graph3 = RD.radialAssign(graph)
+# graph = RD.radialAssign(graph)
 # print graph
 # graph = TD.arrange(graph)
-graph2 = NB.reposition(graph3, False)
+graph = NB.reposition(graph)
 
-TW.tikGraph(graph2, outfile)
+TW.tikGraph(graph, outfile)
 

### 2013-05-03 Graph.py

@@ -163,8 +163,10 @@ class Graph:
             self.AdjacencyList[e.Node1] = [(e.Node2, e.Type)]
         # If node1 does not exist and node2 does:
         elif self.AdjacencyList.get(e.Node1,None) == None:
-            node2 = self.AdjacencyList.keys().get(e.Node2)
-            self.AdjacencyList[e.Node1] = [(node2, e.Type)]
+            # node2 = self.AdjacencyList.keys().get(e.Node2)
+            # self.AdjacencyList[e.Node1] = [(node2, e.Type)]
+            self.AdjacencyList[e.Node1] = []
+            self.AdjacencyList[e.Node2].append((e.Node1, e.Type))
         # If node2 does not exist and node1 does: 
         elif self.AdjacencyList.get(e.Node2,None) == None:
             self.AdjacencyList[e.Node2] = []

### 2013-05-03 Solvers/RadialDisplay.py

@@ -23,7 +23,6 @@ def __recRadial(graph, root, degrees, start, layer, d):
 		if c in visited:
 			continue
 		# if not d:
-		visited.append(c)
 		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
 		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
 
@@ -37,6 +36,9 @@ def __recRadial(graph, root, degrees, start, layer, d):
 		currentDegrees += subDeg
 
 	for(c, t) in children:
+		if c in visited:
+			continue
+		visited.append(c)
 		__recRadial(graph, c, subDeg, currentDegrees, layer+1, d)
 
 

### 2013-05-03 randomgraph.py

@@ -1,0 +1,20 @@
+from random import randint
+
+print "graph large {"
+stuff = list()
+r = randint(1,300)
+for x in xrange(5):
+	y = randint(1,300)
+	if y!=r:
+		print "\t",r,"--", y
+		stuff.append(y)
+
+for x in xrange(200):
+	t = randint(1,300)
+	v = randint(1, len(stuff)-1)
+	if t != stuff[v]:
+		print "\t",stuff[v],"--", t
+		stuff.append(t)
+
+
+print "}"

### 2013-05-03 Graph.py
Fixed Mangos fix for Graph.py

@@ -173,10 +173,14 @@ class Graph:
             self.AdjacencyList[e.Node1] = [(e.Node2, e.Type)]
         # If node1 does not exist and node2 does:
         elif self.AdjacencyList.get(e.Node1,None) == None:
-            # node2 = self.AdjacencyList.keys().get(e.Node2)
-            # self.AdjacencyList[e.Node1] = [(node2, e.Type)]
-            self.AdjacencyList[e.Node1] = []
-            self.AdjacencyList[e.Node2].append((e.Node1, e.Type))
+            nodes = self.AdjacencyList.keys()
+            node2Index = nodes.index(e.Node2)
+            node2 = nodes[node2Index]
+            
+            #node2 = self.AdjacencyList.keys().get(e.Node2)
+            self.AdjacencyList[e.Node1] = [(node2, e.Type)]
+            #self.AdjacencyList[e.Node1] = []
+            #self.AdjacencyList[e.Node2].append((e.Node1, e.Type))
         # If node2 does not exist and node1 does: 
         elif self.AdjacencyList.get(e.Node2,None) == None:
             self.AdjacencyList[e.Node2] = []

### 2013-05-03 JumanG.py

@@ -19,7 +19,8 @@ class JumanG:
         self.Parser = DotParser()
         self.Graph = self.Parser.readFile(infile)
         self.Analysis = GraphAnalysis(self.Graph)
-
+        self.State = 0
+        
     def outputToTikz(self, graph, outfile):
         TW.tikGraph(graph, outfile)
         
@@ -31,6 +32,19 @@ class JumanG:
 
     def runTopDown(self):
         return TD.arrange(self.Graph)
+
+    def chooseSolver(self):
+        self.State = 0
+        return self.State
+
+    def runChosenSolver(self):
+        return {
+            0:self.runNBody(),
+            1:self.runTopDown(),
+            2:self.runRadial(),
+        }[self.State]
+    
+    
 
 if __name__ == "__main__":
     try:
@@ -53,11 +67,13 @@ if __name__ == "__main__":
     # print graph
     # graph = juman.runRadial()
     # print graph
-    graph = juman.runNBody()
+    #graph = juman.runNBody()
     # print graph
 
-    graph = juman.runTopDown()
-    print graph
+    #graph = juman.runTopDown()
+    
+    #graph = juman.runChosenSolver()
+    #print graph
 
     juman.outputToTikz(graph, outfile)
 

### 2013-05-03 BasicDriver.py
radial final

@@ -27,10 +27,10 @@ DP = DotParser()
 DP.readFile(infile)
 graph = DP.Graph
 # print graph
-# graph = RD.radialAssign(graph)
+graph = RD.radialAssign(graph)
 # print graph
 # graph = TD.arrange(graph)
-graph = NB.reposition(graph)
+graph = NB.reposition(graph, False)
 
 TW.tikGraph(graph, outfile)
 

### 2013-05-03 Solvers/RadialDisplay.py

@@ -18,10 +18,14 @@ def __recRadial(graph, root, degrees, start, layer, d):
 
 	subDeg = degrees / len(children)
 	currentDegrees = start
+	toVisit = list()
 
 	for (c, t) in children:
 		if c in visited:
 			continue
+		visited.append(c)
+		toVisit.append(c)
+		# visited.append(c)
 		# if not d:
 		x = layer * armLength * cos(radians(currentDegrees+(subDeg/2)))
 		y = layer * armLength * sin(radians(currentDegrees+(subDeg/2)))
@@ -35,11 +39,15 @@ def __recRadial(graph, root, degrees, start, layer, d):
 		c.PosY = y
 		currentDegrees += subDeg
 
-	for(c, t) in children:
-		if c in visited:
-			continue
-		visited.append(c)
+	currentDegrees = start
+
+	for c in toVisit:
+		# if c in visited:
+		# 	continue
 		__recRadial(graph, c, subDeg, currentDegrees, layer+1, d)
+		currentDegrees += subDeg
+		
+
 
 
 
@@ -66,6 +74,9 @@ def radialAssign(g, sink = False):
 	d = False
 	if graph.Type == 1 :
 		d = True
+
+	# print graph
+	visited.append(gSorted[0])
 
 	# TODO: Add support for multiple roots
 

### 2013-05-03 JumanG.py
current state of the project. The meta-analysis is starting to come together

@@ -13,13 +13,17 @@ import Solvers.TopDownSolver as TD
 
 from sys import argv
 
+
+NBODY = 0
+TOPDOWN = 1
+RADIAL = 2
+
 class JumanG:
-    
     def __init__(self, infile):
         self.Parser = DotParser()
         self.Graph = self.Parser.readFile(infile)
         self.Analysis = GraphAnalysis(self.Graph)
-        self.State = 0
+        self.State = NBODY
         
     def outputToTikz(self, graph, outfile):
         TW.tikGraph(graph, outfile)
@@ -27,23 +31,57 @@ class JumanG:
     def runRadial(self):
         return RD.radialAssign(self.Graph)
 
-    def runNBody(self):
-        return NB.reposition(self.runRadial(),False)
+    def runNBody(self, useRadialSeed = True):
+        if useRadialSeed:
+            return NB.reposition(self.runRadial(),False)
+        else:
+            return NB.reposition(self.Graph,True)
 
     def runTopDown(self):
         return TD.arrange(self.Graph)
 
     def chooseSolver(self):
-        self.State = 0
+        (numberOfNodes,numberOfEdges,numberOfLeaves) = self.Analysis.numberOfNodesEdgesAndLeaves()
+
+        rootNodes = self.Analysis.getRootNodes()
+        numberOfRootNodes = len(rootNodes)
+        hasCycles = True
+        #If it is an acyclic graph, we can run topdown
+        if rootNodes:
+            hasCycles = self.Analysis.BFS(rootNodes[0],True)
+            if not hasCycles:
+                topoList = self.Analysis.topologicalSort(True)
+                treeDepth = topoList[-1][1]
+                
+                print "numberOfNodes",numberOfNodes,"treeDepth",treeDepth
+
+                if numberOfNodes > pow(2,treeDepth+1)-1: 
+                #nodeToDepthRatio = float(numberOfNodes)/treeDepth
+                #if nodeToDepthRatio > 4:
+                    self.State = RADIAL
+                    return self.State
+                else:
+                    self.State = TOPDOWN
+                    return self.State
+
+
+
+        self.State = NBODY
         return self.State
 
-    def runChosenSolver(self):
+    def runChosenSolver(self, choice = None):
+        if choice == None:
+            choice = self.State
         return {
-            0:self.runNBody(),
-            1:self.runTopDown(),
-            2:self.runRadial(),
[…]

### 2013-05-03 Solvers/NBodyRepositioner.py

@@ -65,7 +65,7 @@ def reposition(g, reposition = True):
 
 
 	global armLength
-	armLength = graph.getNumEdges() // 4 + 1
+	armLength = graph.getNumEdges() // 3 + 1
 	# print graph.getNumEdges()
 
 	bestCopy = graph.copy()

### 2013-05-03 Solvers/TopDownSolver.py

@@ -31,8 +31,8 @@ def arrange(g):
 	graph = g.copy()
 	GA = GraphAnalysis(graph)
 	nodepairs = GA.topologicalSort(True)
-        (_,lengthOfGraph) = nodepairs[-1]
-        armLength = 3 / log(lengthOfGraph)
+        #(_,lengthOfGraph) = nodepairs[-1]
+        #armLength = 3 / log(lengthOfGraph)
 
 
 	nodes = list()

### 2013-05-03 Utils.py

@@ -3,6 +3,7 @@
 from pprint import pprint
 from sys import argv
 from copy import deepcopy
+from math import pow
 
 
 def stripAttributes(line):

### 2013-05-03 doc/paper.tex

@@
 Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
-Rarely, however, has it been used to display graphs. We implemented a solver that lays out a graph radially, from the center out.
-These
+It is unusual, however, to use it to display graphs. We wrote our solver to evenly distribute nodes around the root at each level,
+rather than using the traditional style of weighting them based on the number of subnodes as is typical for a solver like this. 
+On graphs that are smaller than
 

### 2013-05-03 doc/paper.tex
added a sentence to paper.tex
Paper stuffs

@@
 \begin{abstract}
-We attempted to display a description of a graph in a nicely formatted 
-We approached this problem using a variety of different algorithms
+There are several available tools available for displaying graphs in an attractive and aesthetically pleasing way, such as Graphviz's products. 
+However, different stratetegies for displaying the graphs are appropriate at different times depending on the features in the graph. Which 
+particular tool to use for any given graph is an exercise left to the user. Our program, JumanG, attempts to take the guesswork out of 
+this process and choose the correct display tool for the graph simply by analyzing the properties of the graph, while providing output that 
+matches or surpasses the quality of the standard set by Graphviz.
 \end{abstract}
@@
 Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
-It is unusual, however, to use it to display graphs. We wrote our solver to evenly distribute nodes around the root at each level,
-rather than using the traditional style of weighting them based on the number of subnodes as is typical for a solver like this. 
-On graphs that are smaller than
+Introduced in 1992 by Eades (EADES CITATION), this layout lays the branches out circularly around the root branching outwards, drawing 
+nodes at different radii from the center. We implemented our own radial solver that uses slightly different techniques than the original
+method. We wrote our solver to evenly distribute nodes around the root at each level, rather than using the traditional style of weighting 
+them based on the number of subnodes as is typical for a solver like this. We also chose to display nodes at their closest level to root. 
+This allows the solver to draw non-tree graphs fairly well; better, in fact, than Graphviz's twopi on these graphs (INSERT COMPARISON GRAPHS) 
+In general, a radial solver is better than a standard layered solver for drawing graphs that are relatively wider than they are deep. Our metric 
+for determining whether the radial solver should be used is given by a measure of width, number of nodes / depth of the graph (put in math eq?) (Juneki
+add more metanalysis here) (Insert some results here)
+
+In addition to the use as an arrangement for directed graphs, we also found that the radial solver worked as an excellent way to presort nodes for the
+Springs Solver, as it spreads the nodes out enough that the nodes resist clumping together.
 
@@
 citation for the springs\cite{springs}
+The springs algorithm, as outlined by (citation), computes a layout for a graph by approximating physics; all nodes repel each and every other node, 
+and edges act as springs to hold the nodes together. This requires deriving values for these forces, as more highly connected graphs will have 
+more edges, and thus more springs, throwing off the balance between the two forces that allows them to be spaced apart. In our solver, we decided
+the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After much 
+experimentation, we determined that the equation to describe the force to be (math eq of total number of edges / total number of nodes +2 tothe 3 /distance tothe 2)
+The spring function was held to simply the distance between the two objects, emulating a spring with a spring constant of 1. We then applied these forces
+to the nodes in the graph, keeping the result with the minimum total force in the system.
+
+In order for these nodes to move freely, however, they must be set to initial positions to react from. (citation of book) suggests 2 possible solutions: 
+Random Placement, and a layout based on geodesic distance. We support both options, the second through the radial placement algorithm as mentioned before.
+The radial placement works well for graphs with less connections, and gives the nodes good starting points to move from. More highly connected graphs,
+however, tend to get stuck in poor positions using this metric, and so for graphs with high connectivity, we default to the random placement. We define 
+connectivity as (total nodes / total edges), and we use the randomized solution on graphs with a connectivity higher than (3?).
+(insert some example graphs)
+
+\subsubsection{Layered Solver}
+Layered graph drawing is an approach to arranging directed acyclic graphs.
 
 \subsection{The Decoder}
-Tikz
+We decided to output our graphs to TikZ syntax, a package for drawing graphs in LaTeX, which we felt was a very appropriate format, and allowed us to ignore the 
+the difficulties of rendering graphics. This also allows us to directly embed our graphs into other LaTeX documents, such as this one. The algorithm for 
+writing the graphs is not particularly clever or efficient, and currently we have only one format, but the TikZ package is featureful enough that adding arbitrary
+features to the display would not be hard.
 

### 2013-05-03 BasicDriver.py

@@ -27,10 +27,10 @@ DP = DotParser()
 DP.readFile(infile)
 graph = DP.Graph
 # print graph
-graph = RD.radialAssign(graph)
+# graph = RD.radialAssign(graph)
 # print graph
 # graph = TD.arrange(graph)
-graph = NB.reposition(graph, False)
+graph = NB.reposition(graph)
 
 TW.tikGraph(graph, outfile)
 

### 2013-05-03 Solvers/NBodyRepositioner.py

@@ -3,21 +3,20 @@ from GraphAnalysis import *
 
 from Utils import *
 from sys import float_info
-
 from random import uniform
 
+# from math import ceil
 #springConst = 1
 k = 1
 armLength = 0
 
 def __calcForces(graph):
 	global armLength
-	# mult = 1
 	if graph.Type ==1:
-		# mult = 16
 		armLength /=2
 	if armLength<2:
 		armLength = 2
+	# armLength = 6
 
 	# print armLength
 	toRet = dict()
@@ -65,7 +64,7 @@ def reposition(g, reposition = True):
 
 
 	global armLength
-	armLength = graph.getNumEdges() // 3 + 1
+	armLength = graph.getNumEdges() / float(len(graph.getNodeList()))+2
 	# print graph.getNumEdges()
 
 	bestCopy = graph.copy()
@@ -74,8 +73,8 @@ def reposition(g, reposition = True):
 	#Added random jitters to all the initial starting points for the nodes
 	if reposition:
 		for node in graph.AdjacencyList:
-			node.PosX += uniform(-1,1)
-			node.PosY += uniform(-1,1)
+			node.PosX += uniform(-.5,.5)
+			node.PosY += uniform(-.5,.5)
 		
 
 	for x in xrange(1000):

### 2013-05-03 doc/paper.tex
wrote some intro

@@
 \begin{abstract}
-There are several available tools available for displaying graphs in an attractive and aesthetically pleasing way, such as Graphviz's products. 
+There are several available tools available for displaying graphs in an attractive and aesthetically pleasing way. 
 However, different stratetegies for displaying the graphs are appropriate at different times depending on the features in the graph. Which 
@@
 this process and choose the correct display tool for the graph simply by analyzing the properties of the graph, while providing output that 
-matches or surpasses the quality of the standard set by Graphviz.
+matches or surpasses the quality provided by the industry standard.
 \end{abstract}
@@
 \section{Introduction}
+Graphs can be used to represent various types of data and information. Graphs come in a variety of shapes and sizes, and as a result, 
+specialized layout methods need to be used with various and sundry types of graphs in order to get a layout that effectively and aesthetically 
+displays the graph. While tools have been developed to to encapsulate these methods, and they work well, they rely on the user to decide which 
+particular tool is necessary for a particular graph, requiring the user to understand properties of the graph in order to properly layout the
+graph. JumanG seeks to eliminate this burden of knowledge by deriving which tool is necessary for displaying the graph by doing analysis on
+the graph itself.
 
+JumanG is currently capable of displaying graphs and digraphs as described by the dot language. We developed three different solvers to handle 
+a variety of types of graphs and display them both clearly and correctly. JumanG outputs into the TikZ format for LaTeX for easy integration into 
+papers like this one.
 \section{Graph Drawing}

### 2013-05-03 doc/paper.tex
abstract and first part of intro

@@
 \begin{abstract}
-There are several available tools available for displaying graphs in an attractive and aesthetically pleasing way. 
-However, different stratetegies for displaying the graphs are appropriate at different times depending on the features in the graph. Which 
-particular tool to use for any given graph is an exercise left to the user. Our program, JumanG, attempts to take the guesswork out of 
-this process and choose the correct display tool for the graph simply by analyzing the properties of the graph, while providing output that 
-matches or surpasses the quality provided by the industry standard.
+In this paper, we attempt to display graphs in an effective or aesthetically pleasing way.
+We implement several types of familiar graph layout methods, and then given a graph we perform some analysis to attempt to decide which method to perform.
+We will compare our implemented graph layout methods to similar GraphViz layout programs, and we will show how our display decision process automatically handles a variety of graphs appropriately.
+
 \end{abstract}
@@
 \section{Introduction}
-Graphs can be used to represent various types of data and information. Graphs come in a variety of shapes and sizes, and as a result, 
-specialized layout methods need to be used with various and sundry types of graphs in order to get a layout that effectively and aesthetically 
-displays the graph. While tools have been developed to to encapsulate these methods, and they work well, they rely on the user to decide which 
-particular tool is necessary for a particular graph, requiring the user to understand properties of the graph in order to properly layout the
-graph. JumanG seeks to eliminate this burden of knowledge by deriving which tool is necessary for displaying the graph by doing analysis on
-the graph itself.
+Graphs can represent a wide range of data and information, and the task of visualizing graphs is important in revealing the patterns and underlying structure within them.
+Although many heuristics are available for what determines a "good" visualization such as number of edge crossings, regular spacing, and node overlaps, in the end the best way to visualize a given graph might be circumstantial or domain specific.
+There are subsequently several specialized layout methods that can perform well in particular instances for effective or aesthetic display.
+
+Programs such as GraphViz have several different layout methods, but it relys on the user to decide which one to use. 
+In other words, the user is required to have an intuition about how each solver works and which one would make their graph appropriately look the best.
+Instead of saying \textit{how} the graph should be displayed, we would want the user to express that the graph should be displayed.
+JumanG seeks to derive which layout method is appropriate by doing some analysis on factors such as the size of the graph, directedness, branching factor, and cyclicity.
 
@@
 papers like this one.
+
+There are several available tools available for displaying graphs in an attractive and aesthetically pleasing way. 
+However, different strategies for displaying the graphs are appropriate at different times depending on the features in the graph. Which 
+particular tool to use for any given graph is an exercise left to the user. Our program, JumanG, attempts to take the guesswork out of 
+this process and choose the correct display tool for the graph simply by analyzing the properties of the graph, while providing output that 
+matches or surpasses the quality provided by the industry standard.
+
 \section{Graph Drawing}
@@
 the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After much 
-experimentation, we determined that the equation to describe the force to be (math eq of total number of edges / total number of nodes +2 tothe 3 /distance tothe 2)
+experimentation, we determined that the equation to describe the force to be (math eq of total number of edges / total number of nodes +2 to the 3 /distance tithe 2)
 The spring function was held to simply the distance between the two objects, emulating a spring with a spring constant of 1. We then applied these forces

### 2013-05-03 doc/paper.tex
paper so far. added a couple of comments

@@
 them based on the number of subnodes as is typical for a solver like this. We also chose to display nodes at their closest level to root. 
-This allows the solver to draw non-tree graphs fairly well; better, in fact, than Graphviz's twopi on these graphs (INSERT COMPARISON GRAPHS) 
+This allows the solver to draw non-tree graphs fairly well; better, in fact, than Graphviz's twopi on these graphs 
+%TODO (INSERT COMPARISON GRAPHS) 
 In general, a radial solver is better than a standard layered solver for drawing graphs that are relatively wider than they are deep. Our metric 
-for determining whether the radial solver should be used is given by a measure of width, number of nodes / depth of the graph (put in math eq?) (Juneki
-add more metanalysis here) (Insert some results here)
+for determining whether the radial solver should be used is given by a measure of width: 
+$$\frac{number_{nodes}}{depth_{graph}}$$
 
-In addition to the use as an arrangement for directed graphs, we also found that the radial solver worked as an excellent way to presort nodes for the
-Springs Solver, as it spreads the nodes out enough that the nodes resist clumping together.
+%TODO add more metanalysis here) (Insert some results here)
+
+In addition to the use as an arrangement for directed graphs, we also found that the radial solver worked as an excellent way to presort nodes for the Springs Solver, because it spreads the nodes out, preventing nodes from clumping together.
 
 \subsubsection{Springs Solver}
+%TODO
 citation for the springs\cite{springs}
+
 The springs algorithm, as outlined by (citation), computes a layout for a graph by approximating physics; all nodes repel each and every other node, 
@@
 more edges, and thus more springs, throwing off the balance between the two forces that allows them to be spaced apart. In our solver, we decided
-the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After much 
-experimentation, we determined that the equation to describe the force to be (math eq of total number of edges / total number of nodes +2 to the 3 /distance tithe 2)
+the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After some 
+experimentation, we used this equation to describe the force: 
+%$$ \frac{number_{edges}}{number_{nodes}^{3}} $$
+%(math eq of total number of edges / total number of nodes +2 to the 3 /distance tithe 2)
+
 The spring function was held to simply the distance between the two objects, emulating a spring with a spring constant of 1. We then applied these forces

### 2013-05-03 JumanG.py
STUFFZ

@@ -17,6 +17,7 @@ from sys import argv
 NBODY = 0
 TOPDOWN = 1
 RADIAL = 2
+NBODYJ = 3
 
 class JumanG:
     def __init__(self, infile):
@@ -47,35 +48,48 @@ class JumanG:
         numberOfRootNodes = len(rootNodes)
         hasCycles = True
         #If it is an acyclic graph, we can run topdown
-        if rootNodes:
-            hasCycles = self.Analysis.BFS(rootNodes[0],True)
-            if not hasCycles:
-                topoList = self.Analysis.topologicalSort(True)
-                treeDepth = topoList[-1][1]
-                
-                print "numberOfNodes",numberOfNodes,"treeDepth",treeDepth
+        if self.Graph.Type==1:
+            if rootNodes:
+                hasCycles = self.Analysis.BFS(rootNodes[0],True)
+                if not hasCycles:
+                    topoList = self.Analysis.topologicalSort(True)
+                    treeDepth = topoList[-1][1]
+                    
+                    print "numberOfNodes",numberOfNodes,"treeDepth",treeDepth
 
-                if numberOfNodes > pow(2,treeDepth+1)-1: 
-                #nodeToDepthRatio = float(numberOfNodes)/treeDepth
-                #if nodeToDepthRatio > 4:
-                    self.State = RADIAL
-                    return self.State
-                else:
-                    self.State = TOPDOWN
-                    return self.State
+                    if numberOfNodes > pow(2,treeDepth+1)-1: 
+                    #nodeToDepthRatio = float(numberOfNodes)/treeDepth
+                    #if nodeToDepthRatio > 4:
+                        self.State = RADIAL
+                        return self.State
+                    else:
+                        self.State = TOPDOWN
+                        return self.State
+        else: # undirected graph
+            # Metric for graph: connectedness: #nodes/#edges, < 3
+            c = self.Graph.getNumEdges()/float(numberOfNodes)
+            print c
+            if c < 3:
+                #radial -> nbody
+                self.State = NBODY
+            else:
+                #nbody random
+                self.State = NBODYJ
 
 
 
-        self.State = NBODY
+
         return self.State
 
     def runChosenSolver(self, choice = None):
         if choice == None:
             choice = self.State
+            print choice
         return {
             NBODY:self.runNBody(),
             TOPDOWN:self.runTopDown(),
[…]

### 2013-05-03 JumanG.py
merged JumanG.py

@@ -15,9 +15,11 @@ from sys import argv
 
 
 NBODY = 0
+NBODY_RADIAL = 10
+NBODY_JITTER = 3
 TOPDOWN = 1
 RADIAL = 2
-NBODYJ = 3
+#NBODYJ = 3
 
 class JumanG:
     def __init__(self, infile):
@@ -67,17 +69,14 @@ class JumanG:
                         return self.State
         else: # undirected graph
             # Metric for graph: connectedness: #nodes/#edges, < 3
-            c = self.Graph.getNumEdges()/float(numberOfNodes)
-            print c
-            if c < 3:
+            connectedness = self.Graph.getNumEdges()/float(numberOfNodes)
+            print connectedness
+            if connectedness < 3:
                 #radial -> nbody
                 self.State = NBODY
             else:
                 #nbody random
-                self.State = NBODYJ
-
-
-
+                self.State = NBODY_JITTER
 
         return self.State
 
@@ -87,15 +86,21 @@ class JumanG:
             print choice
         return {
             NBODY:self.runNBody(),
+            NBODY_RADIAL:self.runNBody(True),
+            NBODY_JITTER:self.runNBody(False),
             TOPDOWN:self.runTopDown(),
             RADIAL:self.runRadial(),
-            NBODYJ:self.runNBody(False),
+            #NBODYJ:self.runNBody(False),
         }.get(choice,self.runNBody())
     
-    #def printChoice(self):
-    #     return {
-   
-    #    }.get(choice)
+    def printChoice(self):
+        return {
+            NBODY:"NBODY",
+            NBODY_RADIAL:"NBODY_RADIAL",
+            NBODY_JITTER:"NBODY_JITTER", 
+            TOPDOWN:"TOPDOWN",
+            RADIAL:"RADIAL",
+        }.get(self.State,"???")
     
 
 if __name__ == "__main__":
@@ -119,16 +124,14 @@ if __name__ == "__main__":
     # print graph
     #graph = juman.runRadial()
     # print graph
-    # graph = juman.runNBody(False)
- #print graph
-
-    #graph = juman.runTopDown()
+    #graph = juman.runNBody(False)
     
     choice = juman.chooseSolver()
-    print choice
+    print choice, juman.printChoice()
 
     graph = juman.runChosenSolver()
-    print graph
+    #print graph
+
     
     juman.outputToTikz(graph, outfile)
 

### 2013-05-03 JumanG.py
asfl;djk

@@ -51,22 +51,21 @@ class JumanG:
         hasCycles = True
         #If it is an acyclic graph, we can run topdown
         if self.Graph.Type==1:
-            if rootNodes:
-                hasCycles = self.Analysis.BFS(rootNodes[0],True)
-                if not hasCycles:
-                    topoList = self.Analysis.topologicalSort(True)
-                    treeDepth = topoList[-1][1]
-                    
-                    print "numberOfNodes",numberOfNodes,"treeDepth",treeDepth
+            hasCycles = self.Analysis.BFS(rootNodes[0],True)
+            if not hasCycles:
+                topoList = self.Analysis.topologicalSort(True)
+                treeDepth = topoList[-1][1]
+                
+                print "numberOfNodes",numberOfNodes,"treeDepth",treeDepth
 
-                    if numberOfNodes > pow(2,treeDepth+1)-1: 
-                    #nodeToDepthRatio = float(numberOfNodes)/treeDepth
-                    #if nodeToDepthRatio > 4:
-                        self.State = RADIAL
-                        return self.State
-                    else:
-                        self.State = TOPDOWN
-                        return self.State
+                if numberOfNodes > pow(3,treeDepth) and numberOfRootNodes==1: 
+                #nodeToDepthRatio = float(numberOfNodes)/treeDepth
+                #if nodeToDepthRatio > 4:
+                    self.State = RADIAL
+                    return self.State
+                else:
+                    self.State = TOPDOWN
+                    return self.State
         else: # undirected graph
             # Metric for graph: connectedness: #nodes/#edges, < 3
             connectedness = self.Graph.getNumEdges()/float(numberOfNodes)

### 2013-05-03 JumanG.py
JumanG and paper

@@ -51,6 +51,8 @@ class JumanG:
         hasCycles = True
         #If it is an acyclic graph, we can run topdown
         if self.Graph.Type==1:
+
+
             hasCycles = self.Analysis.BFS(rootNodes[0],True)
             if not hasCycles:
                 topoList = self.Analysis.topologicalSort(True)
@@ -61,6 +63,7 @@ class JumanG:
                 if numberOfNodes > pow(3,treeDepth) and numberOfRootNodes==1: 
                 #nodeToDepthRatio = float(numberOfNodes)/treeDepth
                 #if nodeToDepthRatio > 4:
+
                     self.State = RADIAL
                     return self.State
                 else:

### 2013-05-03 DotParser.py
circo is now stuck into our code

@@ -7,8 +7,10 @@ from Graph import *
 class DotParser:
    def __init__(self):
       self.Graph = Graph()
-
+      self.FileName = None
+      
    def readFile(self, filename):
+      self.FileName = filename
       FILE = open(filename,'r')
       FILE = FILE.read()
 

### 2013-05-03 JumanG.py

@@ -12,14 +12,17 @@ import Solvers.NBodyRepositioner as NB
 import Solvers.TopDownSolver as TD
 
 from sys import argv
-
+from subprocess import call
 
 NBODY = 0
 NBODY_RADIAL = 10
-NBODY_JITTER = 3
+NBODY_JITTER = 11
 TOPDOWN = 1
 RADIAL = 2
 #NBODYJ = 3
+
+CIRCO = 4
+
 
 class JumanG:
     def __init__(self, infile):
@@ -40,6 +43,13 @@ class JumanG:
         else:
             return NB.reposition(self.Graph,True)
 
+
+    def runCirco(self):
+        outputFile = "a.png"
+        call(["circo","-Tpng",self.Parser.FileName,"-o",outputFile])
+        call(["eog",outputFile])
+        return self.Graph
+
     def runTopDown(self):
         return TD.arrange(self.Graph)
 
@@ -50,9 +60,7 @@ class JumanG:
         numberOfRootNodes = len(rootNodes)
         hasCycles = True
         #If it is an acyclic graph, we can run topdown
-        if self.Graph.Type==1:
-
-
+        if self.Graph.Type==1 and rootNodes:
             hasCycles = self.Analysis.BFS(rootNodes[0],True)
             if not hasCycles:
                 topoList = self.Analysis.topologicalSort(True)
@@ -61,14 +69,15 @@ class JumanG:
                 print "numberOfNodes",numberOfNodes,"treeDepth",treeDepth
 
                 if numberOfNodes > pow(3,treeDepth) and numberOfRootNodes==1: 
-                #nodeToDepthRatio = float(numberOfNodes)/treeDepth
-                #if nodeToDepthRatio > 4:
-
                     self.State = RADIAL
                     return self.State
                 else:
                     self.State = TOPDOWN
                     return self.State
+        #If we have an acyclic graph that has no roots. Its some form of ring.
+        elif self.Graph.Type == 1:
+            self.State = CIRCO
+            return self.State
         else: # undirected graph
             # Metric for graph: connectedness: #nodes/#edges, < 3
             connectedness = self.Graph.getNumEdges()/float(numberOfNodes)
@@ -92,6 +101,8 @@ class JumanG:
             NBODY_JITTER:self.runNBody(False),
             TOPDOWN:self.runTopDown(),
             RADIAL:self.runRadial(),
+            
[…]

### 2013-05-03 JumanG.py
changed the run function to be if-else statements

@@ -94,18 +94,35 @@ class JumanG:
     def runChosenSolver(self, choice = None):
         if choice == None:
             choice = self.State
-            print choice
-        return {
+        
+        #print "TEST",choice, CIRCO
+        
+        if choice == NBODY:
+            return self.runNBody()
+        if choice == NBODY_RADIAL:
+            return self.runNBody(True)
+        if choice == NBODY_JITTER:
+            return self.runNBody(False)
+        if choice == TOPDOWN:
+            return self.runTopDown()
+        if choice == RADIAL:
+            return self.runRadial()
+        if choice == CIRCO:
+            return self.runCirco()
+            
+        return self.runNBody()
+
+        '''return {
             NBODY:self.runNBody(),
             NBODY_RADIAL:self.runNBody(True),
             NBODY_JITTER:self.runNBody(False),
             TOPDOWN:self.runTopDown(),
             RADIAL:self.runRadial(),
-            
             CIRCO:self.runCirco(),
             #NBODYJ:self.runNBody(False),
         }.get(choice,self.runNBody())
-    
+        '''
+
     def printChoice(self):
         return {
             NBODY:"NBODY",
@@ -142,12 +159,16 @@ if __name__ == "__main__":
     #graph = juman.runNBody(False)
     
     choice = juman.chooseSolver()
-    print choice, juman.printChoice()
+    print "choice",choice, juman.printChoice()
+    
+
 
     graph = juman.runChosenSolver()
     #print graph
 
     if choice == CIRCO:
         exit(1)
+
+
     juman.outputToTikz(graph, outfile)
 

### 2013-05-04 BasicDriver.py
Dots and texs

@@ -27,10 +27,10 @@ DP = DotParser()
 DP.readFile(infile)
 graph = DP.Graph
 # print graph
-# graph = RD.radialAssign(graph)
+graph = RD.radialAssign(graph)
 # print graph
 # graph = TD.arrange(graph)
-graph = NB.reposition(graph)
+# graph = NB.reposition(graph)
 
 TW.tikGraph(graph, outfile)
 

### 2013-05-04 doc/paper.tex
lel

@@
 
-The springs algorithm, as outlined by (citation), computes a layout for a graph by approximating physics; all nodes repel each and every other node, 
-and edges act as springs to hold the nodes together. This requires deriving values for these forces, as more highly connected graphs will have 
-more edges, and thus more springs, throwing off the balance between the two forces that allows them to be spaced apart. In our solver, we decided
-the best way to do this was to hold the spring factor constant and to adjust the repulsion force to generate graphs of desired size. After some 
-experimentation, we used this equation to describe the force: 
-%$$ \frac{number_{edges}}{number_{nodes}^{3}} $$
-%(math eq of total number of edges / total number of nodes +2 to the 3 /distance tithe 2)
+The Springs algorithm, as outlined by (citation), computes a layout for a graph by running a physics simulation on the graph.
+All of the nodes are set to repel each other, while the edges are set as ``springs" to hold the nodes together.
+Our solver scales the repelling forces of the nodes based on how densely connected the graphs are, in order to prevent nodes being spaced too close or far apart in the end.
 
-The spring function was held to simply the distance between the two objects, emulating a spring with a spring constant of 1. We then applied these forces
-to the nodes in the graph, keeping the result with the minimum total force in the system.
+The attraction function between two connected nodes is simply a linear factor of the distance between two nodes.
+We put in all of these constraints and then simulated the graph interacting with itself for several iterations, attempting to minimize the total energy in the system.
+
+Finally, the solver also requires the nodes to have an initial configuration. 
+%TODO citation of book
+suggests 2 possible approaches.
+The first being random placement, where all of the nodes are randomized, and the second being based on geodesic distance.
+We have implemented both options, and we use the Radial placement algorithm to
+
+The repulsion force in our Springs Solver:
+$$ \frac{(\frac{number_{edges}}{(number_{nodes})^{3}})}{d^2} $$
+Where d is the euclidean distance between any two nodes.
 
@@
 Layered graph drawing is an approach to arranging directed acyclic graphs.
+
+\subsubsection{Circo Solver}
+Circo is a graph layout solver available from within GraphViz that specializes in arranging circular graphs. 
+We use Circo as one of our available graph solvers because we did not implement our own version of a circular layout solver.
+
+%TODO put in an example picture
+
+In our analysis of the given graph, we can determine that a graph is a directed cycle if there are no root nodes, that is nodes that do not have inward edges pointing to them.
+When a graph is a directed cycle, the Circo Solver tends to have good results.
+Our Springs Solver does a good job with undirected cycles because the edges ``pull" in both directions, and the balanced forces can properly work on the simulation.
 

### 2013-05-04 doc/paper.tex

@@
 \usepackage{url}
+\usepackage{tikz}
 \setlength\titlebox{6.5cm}    % Expanding the titlebox
@@
 \begin{abstract}
-In this paper, we attempt to display graphs in an effective or aesthetically pleasing way.
+In this paper we introduce JumanG, a system that will attempt to display graphs in an effective or aesthetically pleasing way.
 We implement several types of familiar graph layout methods, and then given a graph we perform some analysis to attempt to decide which method to perform.
-We will compare our implemented graph layout methods to similar GraphViz layout programs, and we will show how our display decision process automatically handles a variety of graphs appropriately.
-
+We will compare the results of our implemented graph layout methods to the results of similar GraphViz layout programs, and we will show how our display decision process automatically handles a variety of graphs appropriately.
 \end{abstract}
@@
 
-Programs such as GraphViz have several different layout methods, but it relys on the user to decide which one to use. 
-In other words, the user is required to have an intuition about how each solver works and which one would make their graph appropriately look the best.
-Instead of saying \textit{how} the graph should be displayed, we would want the user to express that the graph should be displayed.
-JumanG seeks to derive which layout method is appropriate by doing some analysis on factors such as the size of the graph, directedness, branching factor, and cyclicity.
+Programs such as GraphViz have several different layout methods, but this relies on the user to decide which one to use. 
+In other words, the user is required to have an intuition about how each solver works and would make their graph appropriately look the best.
+Instead of having the user say \textit{how} the graph should be displayed, we intend to let the user express only that a graph should be displayed.
 
-JumanG is currently capable of displaying graphs and digraphs as described by the dot language. We developed three different solvers to handle 
-a variety of types of graphs and display them both clearly and correctly. JumanG outputs into the TikZ format for LaTeX for easy integration into 
-papers like this one.
+JumanG seeks to determine which layout method is most appropriate by doing some analysis on some features of the graph such as its size, directedness, branching factor, and cyclicity.
 
-There are several available tools available for displaying graphs in an attractive and aesthetically pleasing way. 
-However, different strategies for displaying the graphs are appropriate at different times depending on the features in the graph. Which 
-particular tool to use for any given graph is an exercise left to the user. Our program, JumanG, attempts to take the guesswork out of 
-this process and choose the correct display tool for the graph simply by analyzing the properties of the graph, while providing output that 
-matches or surpasses the quality provided by the industry standard.
+\section{The JumanG Pipeline}
+The JumanG system has three main sections in its pipeline.
+It has an \textit{encoder} that parses in a graph specification into its internal data structures, a set of \textit{solvers} that will lay out the graph and assign coordinate values to display, and a \textit{decoder} that takes the processed graph and outputs out to Tikz LaTeX where it can be displayed on the screen.
 
-\section{Graph Drawing}
+\subsection{The Encoder and the Dot Language}
+The encoder for JumanG starts by reading in a Dot file. 
+Dot is a Little Language used for the specification of graphs, and so we wanted to use Dot files as a graph description for which we could parse in and process.
+We built a parser that accomplishes this, passing off the internal graph to our solvers.
 
-\section{Declarative Pipeline}
+\subsection{Analysis and Solvers}
+We implemented several different graph layout solvers (as well as call one from GraphViz).
+These solvers all implement previous well known layout methods.
+They work well in different situations, and JumanG attempts to decide which of these would be the best to use.
 
-We had an Encoder, Solver, and a Decoder
+In order to do this, JumanG decides based on the features extracted.
+Directed acyclic graphs would be run with the Layered Solver, directed and undirected graphs with very high branching factor would be run with our Radial Solver, directed rings would be run with the GraphViz Circo Solver, and all other undirected graphs and graph meshes would be run with our Springs Solver.
 
-\subsection{The Encoder}
-The Dot Parser
+In this way, we formed a Decision Tree that would allow JumanG's analysis to determine which solver to run the given graph against.
 
-\subsection{The Solvers}
+\subsection{Radial Solver}
+Radial displays have been used to display trees in a way different from a typical top-down approach.
+Introduced in 1992 by Eades (EADES CITATION), this layout places the branches circularly around the root outwards, drawing 
+nodes at different radii from the center. We implemented our own Radial solver that uses similar techniques to the original
+method. We wrote our solver to evenly distribute nodes around the root at each level, rather than the typical style of weighting 
+the nodes based on the subnodes. We also chose to display nodes at their closest level to root. 
+This allows the solver to draw non-tree graphs fairly well. Here is our solver against Graphviz's twopi on some of the same graphs: 
+%TODO (INSERT COMPARISON GRAPHS)
 
-\subsubsection{Radial Solver}
-Radial displays have been used for some time to display trees of various data in a way different from the typical top-down approach.
-Introduced in 1992 by Eades (EADES CITATION), this layout lays the branches out circularly around the root branching outwards, drawing 
-nodes at different radii from the center. We implemented our own radial solver that uses slightly different techniques than the original
-method. We wrote our solver to evenly distribute nodes around the root at each level, rather than using the traditional style of weighting 
-them based on the number of subnodes as is typical for a solver like this. We also chose to display nodes at their closest level to root. 
-This allows the solver to draw non-tree graphs fairly well; better, in fact, than Graphviz's twopi on these graphs 
-%TODO (INSERT COMPARISON GRAPHS) 
-In general, a radial solver is better than a standard layered solver for drawing graphs that are relatively wider than they are deep. Our metric 
+A radial solver can be used rather than a standard layered solver for drawing graphs that are much wider than they are deep. Our metric 
 for determining whether the radial solver should be used is given by a measure of width: 
-$$\frac{number_{nodes}}{depth_{graph}}$$
+$$width = \frac{|nodes|}{depth_{graph}}$$
 
+Here are some results based on our radial solver:
 %TODO add more metanalysis here) (Insert some results here)
 
-In addition to the use as an arrangement for directed graphs, we also found that the radial solver worked as an excellent way to presort nodes for the Springs Solver, because it spreads the nodes out, preventing nodes from clumping together.
+\begin{figure}
+\caption{Radial Solver on a graph with high branching factor}
+\begin{tikzpicture}[scale=0.40, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.4cm]
+	\node (24) at (3.52, 8.28) {24};
+	\node (25) at (1.25, 8.91) {25};
+	\node (26) at (-8.34, -3.37) {26};
+	\node (27) at (-7.55, -4.90) {27};
+	\node (20) at (1.55, -5.80) {20};
+	\node (21) at (3.86, -4.60) {21};
+	\node (22) at (5.20, -3.00) {22};
+	\node (23) at (5.91, -1.04) {23};
+	\node (28) at (-6.89, -5.79) {28};
+	\node (29) at (7.19, -5.42) {29};
+	\node (1) at (0.00, 0.00) {1};
+	\node (3) at (0.00, 3.00) {3};
+	\node (2) at (2.60, 1.50) {2};
+	\node (5) at (-2.60, -1.50) {5};
+	\node (4) at (-2.60, 1.50) {4};
+	\node (7) at (2.60, -1.50) {7};
+	\node (6) at (0.00, -3.00) {6};
+	\node (9) at (5.56, 2.25) {9};
+	\node (8) at (5.96, 0.73) {8};
+	\node (11) at (3.69, 4.73) {11};
+	\node (10) at (4.79, 3.61) {10};
+	\node (13) at (-1.55, 5.80) {13};
+	\node (12) at (1.55, 5.80) {12};
+	\node (15) at (-5.96, -0.73) {15};
+	\node (14) at (-5.20, 3.00) {14};
+	\node (17) at (-4.79, -3.61) {17};
+	\node (16) at (-5.56, -2.25) {16};
+	\node (19) at (-1.55, -5.80) {19};
+	\node (32) at (8.86, -1.56) {32};
+	\node (31) at (8.16, -3.80) {31};
+	\node (30) at (7.71, -4.64) {30};
+	\node (18) at (-3.69, -4.73) {18};
+	\draw [->] (22)--(29);
+	\draw [->] (22)--(30);
+	\draw [->] (22)--(31);
+	\draw [->] (23)--(32);
+	\draw [->] (1)--(2);
+	\draw [->] (1)--(3);
+	\draw [->] (1)--(4);
+	\draw [->] (1)--(5);
+	\draw [->] (1)--(6);
+	\draw [->] (1)--(7);
+	\draw [->] (3)--(12);
+	\draw [->] (3)--(13);
+	\draw [->] (2)--(8);
+	\draw [->] (2)--(9);
+	\draw [->] (2)--(10);
+	\draw [->] (2)--(11);
+	\draw [->] (5)--(15);
+	\draw [->] (5)--(16);
+	\draw [->] (5)--(17);
+	\draw [->] (5)--(18);
+	\draw [->] (4)--(14);
+	\draw [->] (7)--(21);
+	\draw [->] (7)--(22);
+	\draw [->] (7)--(23);
+	\draw [->] (6)--(19);
+	\draw [->] (6)--(20);
+	\draw [->] (12)--(24);
+	\draw [->] (12)--(25);
+	\draw [->] (17)--(27);
+	\draw [->] (17)--(28);
+	\draw [->] (16)--(26);
+\end{tikzpicture}
+\end{figure}
 
-\subsubsection{Springs Solver}
-%TODO
-citation for the springs\cite{springs}
+\subsection{Springs solver}
 
-The Springs algorithm, as outlined by (citation), computes a layout for a graph by running a physics simulation on the graph.
+The Springs algorithm, as outlined by Kawai and Kamada\cite{springs}, computes a layout for a graph by running a physics simulation on the graph.
 All of the nodes are set to repel each other, while the edges are set as ``springs" to hold the nodes together.
@@
 
-The attraction function between two connected nodes is simply a linear factor of the distance between two nodes.
-We put in all of these constraints and then simulated the graph interacting with itself for several iterations, attempting to minimize the total energy in the system.
-
-Finally, the solver also requires the nodes to have an initial configuration. 
-%TODO citation of book
-suggests 2 possible approaches.
-The first being random placement, where all of the nodes are randomized, and the second being based on geodesic distance.
-We have implemented both options, and we use the Radial placement algorithm to
-
-The repulsion force in our Springs Solver:
-$$ \frac{(\frac{number_{edges}}{(number_{nodes})^{3}})}{d^2} $$
+This was the repulsion force used in our Springs solver:
+$$ f_r = \frac{|edges|}{|nodes|}^3 \frac{1}{d^2} $$
 Where d is the euclidean distance between any two nodes.
 
-In order for these nodes to move freely, however, they must be set to initial positions to react from. (citation of book) suggests 2 possible solutions: 
-Random Placement, and a layout based on geodesic distance. We support both options, the second through the radial placement algorithm as mentioned before.
-The radial placement works well for graphs with less connections, and gives the nodes good starting points to move from. More highly connected graphs,
-however, tend to get stuck in poor positions using this metric, and so for graphs with high connectivity, we default to the random placement. We define 
-connectivity as (total nodes / total edges), and we use the randomized solution on graphs with a connectivity higher than (3?).
-(insert some example graphs)
+We defined the attraction function between two connected nodes as a linear factor of the distance between two nodes.
+With the constraints in place the simulation attempts to minimize the total energy in the graph.
 
-\subsubsection{Layered Solver}
+\subsubsection{Springs solver's Initialization}
+The Springs solver also requires the nodes to have an initial configuration. 
+%TODO citation of book
+suggests two possible approaches.
+The first being random placement, where all of the nodes are randomized, and the second being based on geodesic distance.
+We have implemented both options, the second option using the Radial solver as an alternative to this geodesic distance initialization.
+
+The Radial initialization works well for graphs with sparse connections, spreading the nodes out, and giving the Springs algorithm a good starting point to begin minimizing the energy in the system.
+More densly connected graphs do not work as well using this, and so we default back to random jitter perturbation initialization.
+
+We measured connectivity as:
+$$connectivity = \frac{|nodes|}{|edges|}$$
+And based on some empirical testing we determined to use randomized initialization on graphs with connectivity higher than 3.
+
+\begin{figure}
+\caption{A Sparse Graph with the Springs Solver with Radial Initialization}
+\begin{tikzpicture}[scale=0.40, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+	\node (H4) at (0.16, -4.08) {H4};
+	\node (H5) at (-5.44, -2.10) {H5};
+	\node (H2) at (3.43, 8.65) {H2};
+	\node (H3) at (-4.62, 3.79) {H3};
+	\node (H0) at (8.17, 0.76) {H0};
+	\node (H1) at (9.03, 6.64) {H1};
+	\node (C1) at (-1.14, 0.52) {C1};
+	\node (C0) at (4.71, 4.05) {C0};
+	\draw [-] (H4)--(C1);
+	\draw [-] (H5)--(C1);
+	\draw [-] (H2)--(C0);
+	\draw [-] (H3)--(C1);
+	\draw [-] (H0)--(C0);
+	\draw [-] (H1)--(C0);
+	\draw [-] (C1)--(C0);
+	\draw [-] (C1)--(H3);
+	\draw [-] (C1)--(H4);
+	\draw [-] (C1)--(H5);
+	\draw [-] (C0)--(H0);
+	\draw [-] (C0)--(H1);
+	\draw [-] (C0)--(H2);
+	\draw [-] (C0)--(C1);
+\end{tikzpicture}
+\end{figure}
+
+\begin{figure}
+\caption{A Dense Graph with the Springs Solver with Random Jitter Initialization}
+\begin{tikzpicture}[scale=0.50, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+	\node (k3) at (0.72, 3.87) {k3};
+	\node (k2) at (-3.06, -2.52) {k2};
+	\node (k1) at (1.41, -3.52) {k1};
+	\node (k5) at (-3.49, 2.05) {k5};
+	\node (k4) at (3.75, 0.43) {k4};
+	\draw [-] (k3)--(k1);
+	\draw [-] (k3)--(k2);
+	\draw [-] (k3)--(k4);
+	\draw [-] (k3)--(k5);
+	\draw [-] (k2)--(k1);
+	\draw [-] (k2)--(k3);
+	\draw [-] (k2)--(k4);
+	\draw [-] (k2)--(k5);
+	\draw [-] (k1)--(k2);
+	\draw [-] (k1)--(k3);
+	\draw [-] (k1)--(k4);
+	\draw [-] (k1)--(k5);
+	\draw [-] (k5)--(k1);
+	\draw [-] (k5)--(k2);
+	\draw [-] (k5)--(k3);
+	\draw [-] (k5)--(k4);
+	\draw [-] (k4)--(k1);
+	\draw [-] (k4)--(k2);
+	\draw [-] (k4)--(k3);
+	\draw [-] (k4)--(k5);
+\end{tikzpicture}
+\end{figure}
+
+\subsection{Layered Solver}
 Layered graph drawing is an approach to arranging directed acyclic graphs.
 
-\subsubsection{Circo Solver}
+\subsection{Circo Solver}
 Circo is a graph layout solver available from within GraphViz that specializes in arranging circular graphs. 

### 2013-05-04 doc/paper.tex
paper.tex. Added more figures

@@
 \usepackage{tikz}
+
+\usepackage[english]{babel}
+\usepackage{graphicx}
 \setlength\titlebox{6.5cm}    % Expanding the titlebox
@@
 \begin{figure}
-\caption{A Sparse Graph with the Springs Solver with Radial Initialization}
+\caption{A Sparsely Connected Graph with the Springs Solver with Radial Initialization}
 \begin{tikzpicture}[scale=0.40, transform shape]
@@
 \begin{figure}
-\caption{A Dense Graph with the Springs Solver with Random Jitter Initialization}
+\caption{A Densely Connected Graph with the Springs Solver with Random Jitter Initialization}
 \begin{tikzpicture}[scale=0.50, transform shape]
@@
 %TODO put in an example picture
+\begin{figure}[h!]
+\caption{A Ring Graph solved by the Circo Solver}
+\centering
+\includegraphics[width=0.3\textwidth]{circo.jpg}
+\end{figure}
 
@@
 Our Springs Solver does a good job with undirected cycles because the edges ``pull" in both directions, and the balanced forces can properly work on the simulation.
+
+\begin{figure}
+\caption{The same Undirected Ring Graph solved by the Springs Solver}
+\begin{tikzpicture}[scale=0.40, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+	\node (n0) at (-0.17, -0.79) {n0};
+	\node (n1) at (-0.17, 4.10) {n1};
+	\node (n2) at (4.06, 6.54) {n2};
+	\node (n3) at (8.30, 4.09) {n3};
+	\node (n4) at (8.30, -0.80) {n4};
+	\node (n5) at (4.06, -3.24) {n5};
+	\draw [-] (n0)--(n1);
+	\draw [-] (n0)--(n5);
+	\draw [-] (n1)--(n0);
+	\draw [-] (n1)--(n2);
+	\draw [-] (n2)--(n1);
+	\draw [-] (n2)--(n3);
+	\draw [-] (n3)--(n2);
+	\draw [-] (n3)--(n4);
+	\draw [-] (n4)--(n3);
+	\draw [-] (n4)--(n5);
+	\draw [-] (n5)--(n4);
+	\draw [-] (n5)--(n0);
+\end{tikzpicture}
+\end{figure}
 

### 2013-05-04 doc/paper.tex
Added more figures to the paper.
serp

@@
 Radial displays have been used to display trees in a way different from a typical top-down approach.
-Introduced in 1992 by Eades (EADES CITATION), this layout places the branches circularly around the root outwards, drawing 
+Introduced in 1992 by Eades \cite{freeTrees}, this layout places the branches circularly around the root outwards, drawing 
 nodes at different radii from the center. We implemented our own Radial solver that uses similar techniques to the original
@@
 the nodes based on the subnodes. We also chose to display nodes at their closest level to root. 
-This allows the solver to draw non-tree graphs fairly well. Here is our solver against Graphviz's twopi on some of the same graphs: 
-%TODO (INSERT COMPARISON GRAPHS)
+This allows the solver to draw non-tree graphs fairly well. In some instances, we can even beat Graphviz's twopi instantiation, detailed below in our experimental comparison section. %TODO wording
 
@@
 \subsubsection{Springs solver's Initialization}
-The Springs solver also requires the nodes to have an initial configuration. 
-%TODO citation of book
+The Springs solver also requires the nodes to have an initial configuration. Wilkinson \cite{grammarGraphics}
+%TODO style?
 suggests two possible approaches.
@@
 
+In most cases, we match Graphviz's implementation, such as in rendering a Sierpinski triangle:
+
+\begin{figure}[h!]
+\caption{GraphViz's neato solver's version of a Sierpinski triangle}
+\centering
+\includegraphics[width=0.3\textwidth]{serp.png}
+\end{figure}
+
+\begin{figure}
+\caption{Our Spring Solver's version of the same Sierpinski triangle}
+\begin{tikzpicture}[scale=0.40, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+	\node (1) at (4.55, -4.87) {1};
+	\node (3) at (-6.33, -1.86) {3};
+	\node (2) at (1.72, 6.06) {2};
+	\node (5) at (2.95, 0.54) {5};
+	\node (4) at (-0.84, -3.18) {4};
+	\node (6) at (-2.16, 1.96) {6};
+	\draw [-] (1)--(4);
+	\draw [-] (1)--(5);
+	\draw [-] (3)--(4);
+	\draw [-] (3)--(6);
+	\draw [-] (2)--(5);
+	\draw [-] (2)--(6);
+	\draw [-] (5)--(1);
+	\draw [-] (5)--(2);
+	\draw [-] (5)--(4);
+	\draw [-] (5)--(6);
+	\draw [-] (4)--(1);
+	\draw [-] (4)--(3);
+	\draw [-] (4)--(5);
+	\draw [-] (4)--(6);
+	\draw [-] (6)--(2);
+	\draw [-] (6)--(3);
+	\draw [-] (6)--(4);
+	\draw [-] (6)--(5);
+\end{tikzpicture}
+
+In some cases, we can even beat GraphViz's performance by a small margin:
+
+\begin{figure}[h!]
+\caption{GraphViz's 2Pi Radial Solver's version of an example graph}
+\centering
+\includegraphics[width=0.3\textwidth]{turnip_dag.png}
+\end{figure}
+
+\begin{figure}
+\caption{Our Radial Solver's version of the example graph. Compared to 2Pi.}
+\begin{tikzpicture}[scale=0.70, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+	\node (Steve) at (0.00, 0.00) {Steve};
+	\node (Louis) at (0.00, -3.00) {Louis};
+	\node (Katrina) at (-4.24, 4.24) {Katrina};
+	\node (Danielle) at (0.00, 3.00) {Danielle};
+	\node (Vivian) at (4.24, 4.24) {Vivian};
+	\draw [->] (Steve)--(Danielle);
+	\draw [->] (Steve)--(Louis);
+	\draw [->] (Danielle)--(Vivian);
+	\draw [->] (Danielle)--(Katrina);
+	\draw [->] (Vivian)--(Katrina);
+\end{tikzpicture}
+\end{figure}
+
 \section{Future Work}

### 2013-05-04 doc/paper.tex
paper so far

@@
 Here are some results based on our radial solver:
-%TODO add more metanalysis here) (Insert some results here)
 
@@
 \caption{A Densely Connected Graph with the Springs Solver with Random Jitter Initialization}
-\begin{tikzpicture}[scale=0.50, transform shape]
+\begin{tikzpicture}[scale=0.70, transform shape]
 	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
@@
 \subsection{Layered Solver}
-Layered graph drawing is an approach to arranging directed acyclic graphs.
+Layered graph, or Sugiyama-style drawing is an approach to arranging directed acyclic graphs\cite{sugiyama}.
+This drawing approach relies on assigning the nodes to a ``layer" in the graph and then assigning descending y-coordinates for each successive layer from the root.
+Then, for each layer, the nodes are rearranged to minimize the edge crossings in between layers.
+
+Our implementation of a Layered Solver assigns its layers determined by a ``topological ordering" starting with the root nodes of the DAG.
+We topologically sort the graph, but all of the nodes are marked with the iteration at which they were added to the sorted list.
+
+After determining all of the layers, the nodes in each layer are rearranged in an attempt to minimize edge crossings.
+Determining an ordering that minimizes edge crossings is NP-Complete\cite{EdgeCrossings}, and so we rely on heuristics to accomplish this task.
+
+\begin{figure}
+\caption{A Directed Acyclic Graph with the Layered Solver}
+\begin{tikzpicture}[scale=0.70, transform shape]
+	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+	\node (a) at (0.00, 0.00) {a};
+	\node (c) at (1.50, -3.00) {c};
+	\node (b) at (-1.50, -3.00) {b};
+	\node (e) at (3.00, -6.00) {e};
+	\node (d) at (-3.00, -6.00) {d};
+	\node (f) at (0.00, -6.00) {f};
+	\node (c2) at (4.50, -3.00) {c2};
+	\node (c1) at (-4.50, -3.00) {c1};
+	\draw [->] (a)--(b);
+	\draw [->] (a)--(c);
+	\draw [->] (a)--(c1);
+	\draw [->] (a)--(c2);
+	\draw [->] (c)--(e);
+	\draw [->] (c)--(f);
+	\draw [->] (b)--(d);
+	\draw [->] (b)--(e);
+	\draw [->] (b)--(f);
+	\draw [->] (b)--(d);
+	\draw [->] (c2)--(e);
+	\draw [->] (c1)--(d);
+\end{tikzpicture}
+\end{figure}
+
+\subsubsection{Edge Crossing Minimization Heuristic}
+The heuristic our Layerd Solver used to order nodes and minimize edge crossings between layers relies on a calculation analogous to ``center of mass" using the edges between the surrounding layers.
+Each node is assigned an averaged index interpolating between the indexes of all the adjacent nodes above and below the layer, and then the nodes are sorted based on these indexes.
+
+\begin{figure}
+\caption{Edge Crossing Heuristic Illustration}\label{layers}
+\centering
+\includegraphics[width=0.52\textwidth]{layereddia.png}
+\end{figure}
+
+From Figure~\ref{layers}, our index calculations are as such.
+
+$$ index(L_i , n_j) = \frac{\sum\limits_a index(L_{i-1}n_a) + \sum\limits_b index(L_{i+1}n_b)}{|L_{i-1}n_a| + |L_{i+1}n_b|}$$
+$$\forall Edge(n_a , n_j), Edge(n_j , n_b)$$
+This heuristic is greedy in that at each layer we try to place nodes closer to its adjacent nodes.
 
@@
 When a graph is a directed cycle, the Circo Solver tends to have good results.
-Our Springs Solver does a good job with undirected cycles because the edges ``pull" in both directions, and the balanced forces can properly work on the simulation.
 
-\begin{figure}
-\caption{The same Undirected Ring Graph solved by the Springs Solver}
-\begin{tikzpicture}[scale=0.40, transform shape]
-	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
-	\node (n0) at (-0.17, -0.79) {n0};
-	\node (n1) at (-0.17, 4.10) {n1};
-	\node (n2) at (4.06, 6.54) {n2};
-	\node (n3) at (8.30, 4.09) {n3};
-	\node (n4) at (8.30, -0.80) {n4};
-	\node (n5) at (4.06, -3.24) {n5};
-	\draw [-] (n0)--(n1);
-	\draw [-] (n0)--(n5);
-	\draw [-] (n1)--(n0);
-	\draw [-] (n1)--(n2);
-	\draw [-] (n2)--(n1);
-	\draw [-] (n2)--(n3);
-	\draw [-] (n3)--(n2);
-	\draw [-] (n3)--(n4);
-	\draw [-] (n4)--(n3);
-	\draw [-] (n4)--(n5);
-	\draw [-] (n5)--(n4);
-	\draw [-] (n5)--(n0);
-\end{tikzpicture}
-\end{figure}
+For undirected cycles, our Spring Solver does a good job because the edges ``pull" in both directions, and so the balanced forces can properly work on the simulation.
+In JumanG, we use our Spring Solver when we detect such undirected cycles.
 
-\subsection{The Decoder}
-We decided to output our graphs to TikZ syntax, a package for drawing graphs in LaTeX, which we felt was a very appropriate format, and allowed us to ignore the 
-the difficulties of rendering graphics. This also allows us to directly embed our graphs into other LaTeX documents, such as this one. The algorithm for 
-writing the graphs is not particularly clever or efficient, and currently we have only one format, but the TikZ package is featureful enough that adding arbitrary
-features to the display would not be hard.
+%\begin{figure}
+%\caption{The same Undirected Ring Graph solved by the Springs Solver}
+%\begin{tikzpicture}[scale=0.40, transform shape]
+%	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
+%	\node (n0) at (-0.17, -0.79) {n0};
+%	\node (n1) at (-0.17, 4.10) {n1};
+%	\node (n2) at (4.06, 6.54) {n2};
+%	\node (n3) at (8.30, 4.09) {n3};
+%	\node (n4) at (8.30, -0.80) {n4};
+%	\node (n5) at (4.06, -3.24) {n5};
+%	\draw [-] (n0)--(n1);
+%	\draw [-] (n0)--(n5);
+%	\draw [-] (n1)--(n0);
+%	\draw [-] (n1)--(n2);
+%	\draw [-] (n2)--(n1);
+%	\draw [-] (n2)--(n3);
+%	\draw [-] (n3)--(n2);
+%	\draw [-] (n3)--(n4);
+%	\draw [-] (n4)--(n3);
+%	\draw [-] (n4)--(n5);
+%	\draw [-] (n5)--(n4);
+%	\draw [-] (n5)--(n0);
+%\end{tikzpicture}
+%\end{figure}
+
+\subsection{The Decoder: TikZ}
+After our analysis for choosing the solver and after running the chosen solver, JumanG outputs the processed graph out to TikZ LaTeX.
+TikZ is a graphics package we could manipulate directly to draw the nodes and edges at all the specified coordinates to represent the graph.
+
+By default, the decoder creates the output file that fills out an entire page of a document. The examples embedded in this paper have been scaled down.
 
@@
 
-In most cases, we match Graphviz's implementation, such as in rendering a Sierpinski triangle:
+In many cases, our graph layout solvers perform comparatively to Graphviz solvers. For example here is a rendering of a Sierpinski triangle:
 
@@
 \end{tikzpicture}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{turnip_dag.png}
+\includegraphics[width=0.15\textwidth]{turnip_dag.png}
 \end{figure}
@@
 \caption{Our Radial Solver's version of the example graph. Compared to 2Pi.}
-\begin{tikzpicture}[scale=0.70, transform shape]
+\begin{tikzpicture}[scale=0.60, transform shape]
 	\tikzstyle{every node} = [circle, fill=gray!30, minimum size = 1.8cm]
@@
 \section{Future Work}
+JumanG could be extended in a variety of ways that may be interesting. 
+On a basic level, more solvers could be implemented and a more nuanced analysis could be used to choose among them.
+But instead of developing the solver decision tree by hand, we could try to learn parameters that determine which graph layouts are more favorable than others.
+
+Using our graph analysis toolkit, we extracted out a set of features such as the size of the graph, its directedness, and its branching factor.
+We could also go further and have additional features such as the number of strongly connected components, diameter, or whether the graph is bipartite.
+
+\subsection{Scalability}
+Currently, JumanG was developed in consideration with relatively small graphs.
+
+-Auto-scaling on graphs and nodes.
+-More Solvers
+-More detailed decision heuristics (Mechanical Turk)
+-Greater Display Features / Dot Syntax support
 

### 2013-05-04 doc/paper.tex
paper so far

@@
 JumanG could be extended in a variety of ways that may be interesting.
-On a basic level, more solvers could be implemented and a more nuanced analysis could be used to choose among them.
-But instead of developing the solver decision tree by hand, we could try to learn parameters that determine which graph layouts are more favorable than others.
 
-Using our graph analysis toolkit, we extracted out a set of features such as the size of the graph, its directedness, and its branching factor.
-We could also go further and have additional features such as the number of strongly connected components, diameter, or whether the graph is bipartite.
+\subsection{Learned Analysis Parameters}
+Instead of developing the solver decision tree by hand, we could try to learn parameters that determine which graph layouts are more favorable than others.
 
-\subsection{Scalability}
-Currently, JumanG was developed in consideration with relatively small graphs.
+Using our graph analysis toolkit, we can extract a set of features of a graph such as its size, directedness, and branching factor.
+We could also go expand this and have additional features such as the strongly connected components, diameter, or bipartiteness.
 
--Auto-scaling on graphs and nodes.
--More Solvers
--More detailed decision heuristics (Mechanical Turk)
--Greater Display Features / Dot Syntax support
+We could learn which parameters determine which graph layouts are the best.
+We could generate a large set of random graphs, and process all of them with each of our graph layout solvers.
+We could get annotated data by using a service like Mechanical Turk, presenting every solver's representation of each graph side-by-side and asking the users to choose the graph layout the best visualizes the data.
 
-\section{Conclusions}
+Using the analysis features, we could develop a multi-class classifier to learn which graph layouts are the best for any arbitrary graph.
+
+\subsection{Handling and Displaying more Dot Features}
+This project was primarily focused on graph layout, but the Dot Language can support much richer features such as edge labels, node labels, and node colors.
+Further work could include expanding our parser to handle anything within the Dot Language.
+We could also allow the user to set the positions of some of the nodes and then solve around them.
+
+\subsection{Additional Solvers}
+On a basic level, more solvers could be implemented and the analysis could further developed be used to choose among them.
+Additional Solvers might handle arranging graphs in N-dimensions, and the analysis could determine to use such a solver if the graph was sufficiently non-planar.
+
+\section{Conclusion}
+Graph drawing can be difficult due to the wildly varying expectations from different users and domains.
 

### 2013-05-04 doc/paper.tex
paper is almost finished

@@
 
-In many cases, our graph layout solvers perform comparatively to Graphviz solvers. For example here is a rendering of a Sierpinski triangle:
-
 \begin{figure}[h!]
 \caption{GraphViz's neato solver's version of a Sierpinski triangle}
+\label{neatoSierpinski}
 \centering
@@
 \begin{figure}
-\caption{Our Spring Solver's version of the same Sierpinski triangle}
+\caption{Our Spring Solver's version of a Sierpinski triangle}
+\label{springSierpinski}
 \begin{tikzpicture}[scale=0.40, transform shape]
@@
 
-In some cases, we can even beat GraphViz's performance by a small margin:
+In many cases, our graph layout solvers perform comparatively to Graphviz solvers.
+For example, in Figure~\ref{neatoSierpinski} we show GraphViz's ``neato" Spring Solver, compared to Figure~\ref{springSierpinski}.
+We render a Sierpinski triangle, automatically choosing the Springs solver with random jitter initialization.
 
@@
 \caption{GraphViz's 2Pi Radial Solver's version of an example graph}
+\label{twopiTurnip}
 \centering
@@
 \caption{Our Radial Solver's version of the example graph. Compared to 2Pi.}
+\label{radialTurnip}
 \begin{tikzpicture}[scale=0.60, transform shape]
@@
 \end{figure}
+
+In some cases, JumanG's solvers displayed graphs more effectively than comparable GraphViz solvers, as in Figure~\ref{twopiTurnip} and in Figure~\ref{radialTurnip}.
 
@@
 \section{Conclusion}
-Graph drawing can be difficult due to the wildly varying expectations from different users and domains.
+Graph drawing can be difficult due to its underspecified nature.
+Across different users and domains there can be varying expectations and requirements.
+In this respect, trying to effectively represent any graph for any user might be intractible.
+However, JumanG attempts to handle this task anyway, achieving some good results on a variety of inputs.
+It does this by determining which layout is most appropriate to the input graph.
 

### 2013-05-04 doc/paper.tex
final version for submission

@@
 
-\subsection{Radial Solver}
-Radial displays have been used to display trees in a way different from a typical top-down approach.
-Introduced in 1992 by Eades \cite{freeTrees}, this layout places the branches circularly around the root outwards, drawing 
-nodes at different radii from the center. We implemented our own Radial solver that uses similar techniques to the original
-method. We wrote our solver to evenly distribute nodes around the root at each level, rather than the typical style of weighting 
-the nodes based on the subnodes. We also chose to display nodes at their closest level to root. 
-This allows the solver to draw non-tree graphs fairly well. In some instances, we can even beat Graphviz's twopi instantiation, detailed below in our experimental comparison section. %TODO wording
-
-A radial solver can be used rather than a standard layered solver for drawing graphs that are much wider than they are deep. Our metric 
-for determining whether the radial solver should be used is given by a measure of width: 
-$$width = \frac{|nodes|}{depth_{graph}}$$
-
-Here are some results based on our radial solver:
-
 \begin{figure}
 \caption{Radial Solver on a graph with high branching factor}
+\label{sprawl}
 \begin{tikzpicture}[scale=0.40, transform shape]
@@
 
+\subsection{Radial Solver}
+
+Radial displays have been used to display trees in a way different from a typical top-down approach.
+Introduced in 1991 by Eades \cite{Eades:91} %~\cite{freeTrees}, 
+this layout places the branches circularly around the root outwards, drawing 
+nodes at different radii from the center. We implemented our own Radial solver that uses similar techniques to the original
+method. We wrote our solver to evenly distribute nodes around the root at each level, rather than the typical style of weighting 
+the nodes based on the subnodes. We also chose to display nodes at their closest level to root. 
+This allows the solver to draw non-tree graphs fairly well. In some instances, we can even beat Graphviz's twopi instantiation, detailed below in our experimental comparison section. %TODO wording
+
+A radial solver can be used rather than a standard layered solver for drawing graphs that are much wider than they are deep. Our metric 
+for determining whether the radial solver should be used is given by a measure of width: 
+$$width = \frac{|nodes|}{depth_{graph}}$$
+
+You can see a graph drawn using our radial solver in Figure~\ref{sprawl}.
+
 \subsection{Springs solver}
 
-The Springs algorithm, as outlined by Kawai and Kamada\cite{springs}, computes a layout for a graph by running a physics simulation on the graph.
+The Springs algorithm, as outlined by Kawai and Kamada \cite{Kamada:89}, computes a layout for a graph by running a physics simulation on the graph.
 All of the nodes are set to repel each other, while the edges are set as ``springs" to hold the nodes together.
@@
 \subsubsection{Springs solver's Initialization}
-The Springs solver also requires the nodes to have an initial configuration. Wilkinson \cite{grammarGraphics}
-%TODO style?
-suggests two possible approaches.
+The Springs solver also requires the nodes to have an initial configuration.
+Wilkinson suggests two possible approaches \cite{Wilkinson:05}.
 The first being random placement, where all of the nodes are randomized, and the second being based on geodesic distance.
@@
 $$connectivity = \frac{|nodes|}{|edges|}$$
-And based on some empirical testing we determined to use randomized initialization on graphs with connectivity higher than 3.
+Based on empirical testing we determined to use randomized initialization on graphs with connectivity higher than 3.
 
@@
 \subsection{Layered Solver}
-Layered graph, or Sugiyama-style drawing is an approach to arranging directed acyclic graphs\cite{sugiyama}.
+Layered graph, or Sugiyama-style drawing is an approach to arranging directed acyclic graphs \cite{Sugiyama:81}.
 This drawing approach relies on assigning the nodes to a ``layer" in the graph and then assigning descending y-coordinates for each successive layer from the root.
@@
 After determining all of the layers, the nodes in each layer are rearranged in an attempt to minimize edge crossings.
-Determining an ordering that minimizes edge crossings is NP-Complete\cite{EdgeCrossings}, and so we rely on heuristics to accomplish this task.
+Determining an ordering that minimizes edge crossings is NP-Complete \cite{Eades:94}, and so we rely on heuristics to accomplish this task.
 
@@
 \subsubsection{Edge Crossing Minimization Heuristic}
-The heuristic our Layerd Solver used to order nodes and minimize edge crossings between layers relies on a calculation analogous to ``center of mass" using the edges between the surrounding layers.
+The heuristic our Layered Solver used to order nodes and minimize edge crossings between layers relies on a calculation analogous to ``center of mass" using the edges between the surrounding layers.
 Each node is assigned an averaged index interpolating between the indexes of all the adjacent nodes above and below the layer, and then the nodes are sorted based on these indexes.
@@
 
-\bibliographystyle{plain}
-\bibliography{citations}
+%\bibliographystyle{plain}
+%\bibliography{citations}
+\begin{thebibliography}{}
+
+%springs
+\bibitem[\protect\citename{Kamada and Kawai}1989]{Kamada:89}
+Tomihisa Kamada and Satoru Kawai.
+\newblock 1989.
+\newblock {\em An Algorithm for Drawing General Undirected Graphs}, volume~31.
+\newblock Information Processing Letters.
+
+%grammerGraphics
+\bibitem[\protect\citename{Wilkinson}2005]{Wilkinson:05}
+Leland Wilkinson
+\newblock 2005.
+\newblock {\em The Grammar of Graphics}.
+\newblock Springer Science+Business Media, Inc.
+
+%radial
+\bibitem[\protect\citename{Eades}1991]{Eades:91}
+Peter Eades
+\newblock 1991.
+\newblock {\em Drawing Free Trees}.
+\newblock International Institute for Advanced Study of Social Information Science, Fujitsu Limited.
+
+% edgecrossings is NP
+\bibitem[\protect\citename{Eades}1994]{Eades:94}
+Eades, Peter and Wormald, Nicholas C.
+\newblock 1994.
+\newblock {\em Edge crossings in drawings of bipartite graphs}, volume~11.
+\newblock Springer-Verlag.
+
+%layered
+\bibitem[\protect\citename{Sugiyama}1981]{Sugiyama:81}
+Kozo Sugiyama
+\newblock 1981.
+\newblock {\em Methods for Visual Understanding of Hierarchical System Structures}, volume~11.
+\newblock IEEE Transactions on Systems, Man, and Cybernetics.
 

### 2013-05-04 BasicDriver.py
removed stuff

@@ -1,36 +1,0 @@
-#!/usr/bin/python
-
-from Graph import *
-
-import Solvers.RadialDisplay as RD
-import TikzWriter as TW
-import sys
-from DotParser import *
-import Solvers.NBodyRepositioner as NB
-import Solvers.TopDownSolver as TD
-
-argv = sys.argv
-
-infile = ""
-outfile = ""
-if len(argv) !=3 :
-	print "Usage: BasicDriver inputfile outputfile"
-	sys.exit()
-
-else:
-	infile = argv[1]
-	outfile = argv[2]
-
-directed = False
-DP = DotParser()
-
-DP.readFile(infile)
-graph = DP.Graph
-# print graph
-graph = RD.radialAssign(graph)
-# print graph
-# graph = TD.arrange(graph)
-# graph = NB.reposition(graph)
-
-TW.tikGraph(graph, outfile)
-

### 2013-05-04 randomgraph.py

@@ -1,20 +1,0 @@
-from random import randint
-
-print "graph large {"
-stuff = list()
-r = randint(1,300)
-for x in xrange(5):
-	y = randint(1,300)
-	if y!=r:
-		print "\t",r,"--", y
-		stuff.append(y)
-
-for x in xrange(200):
-	t = randint(1,300)
-	v = randint(1, len(stuff)-1)
-	if t != stuff[v]:
-		print "\t",stuff[v],"--", t
-		stuff.append(t)
-
-
-print "}"
